---
title: "Manyglm_varpart"
author: "Rodolfo Pelinson"
date: "`r Sys.Date()`"
output: 
  github_document: 
    fig_width: 10
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE}
dir<-("C:/Users/rodol/OneDrive/repos/Urban_fish_assemblages")
```

Loading important functions and packages

```{r, warning=FALSE}
source(paste(sep = "/",dir,"functions/remove_sp.R"))
source(paste(sep = "/",dir,"functions/R2_manyglm.R"))
source(paste(sep = "/",dir,"functions/forward_sel_manyglm.R"))
source(paste(sep = "/",dir,"functions/varpart_manyglm.R"))
source(paste(sep = "/",dir,"functions/My_coefplot.R"))
source(paste(sep = "/",dir,"functions/letters.R"))
source(paste(sep = "/",dir,"functions/at_generator.R"))



library(mvabund)
library(vegan)
library(yarrr)
library(ade4)
library(adespatial)
library(corrplot)
library(colorspace)

set.seed(1)
```

Loading data

```{r, warning=FALSE, message =FALSE}
assembleia_peixes <- read.csv(paste(sep = "/",dir,"data/com_por_bacia.csv"), row.names = 1)
agua_PCs <- read.csv(paste(sep = "/",dir,"data/pcas_amb/agua_PCs.csv"), row.names = 1)
estrutura_PCs <- read.csv(paste(sep = "/",dir,"data/pcas_amb/estrutura_PCs.csv"), row.names = 1)
bacia_PCs <- read.csv(paste(sep = "/",dir,"data/pcas_amb/bacia_PCs.csv"), row.names = 1)
delineamento <- read.csv(paste(sep = "/",dir,"data/delineamento.csv"))
dist_euclid <- read.csv(paste(sep = "/",dir,"data/dist/Matriz_distancia_matriz_euclidiana.csv"), row.names = 1)




```

Removing species with less than 2 presences and combining them into the artificial "Singletons and doubletons" species.

```{r, warning=FALSE, message = FALSE}
assembleia_peixes <- read.csv(paste(sep = "/",dir,"data/com_por_bacia.csv"), row.names = 1)
assembleia_peixes <- assembleia_peixes[,-c(4,11)]
assembleia_peixes_rm <- remove_sp(com = assembleia_peixes, n_sp = 2)

singletons_doubletons <- remove_sp(assembleia_peixes, 2, less_equal = TRUE)
doubletons <- remove_sp(singletons_doubletons, 1)

singletons <- remove_sp(assembleia_peixes, 1, less_equal = TRUE)

sing_doub_ab <- rowSums(singletons_doubletons)
sing_ab <- rowSums(singletons)

sing_doub <- rowSums(decostand(singletons_doubletons, method = "pa")) 
sing <- rowSums(decostand(singletons, method = "pa")) 

assembleia_peixes_rm <- data.frame(assembleia_peixes_rm, Singletons_and_doubletons = sing_doub_ab)
```

Preparing and standardizing predictors

```{r, warning=FALSE, message = FALSE}
urb <- data.frame(urb = delineamento$urbana)

urb <- decostand(urb, method = "stand")
agua_PCs <- decostand(agua_PCs, method = "stand")
estrutura_PCs <- decostand(estrutura_PCs, method = "stand")
bacia_PCs <- decostand(bacia_PCs, method = "stand")
```

Producing spatial filters

```{r, warning=FALSE}
dist_euclid <- as.dist(dist_euclid)

dbmem_euclid <- dbmem(dist_euclid, thresh = NULL, MEM.autocor = c("positive", "non-null", "all", "negative"), store.listw = TRUE, silent = FALSE)

dbmem_euclid <- decostand(dbmem_euclid, method = "stand")
```

Checking if the rows of all data frames match

```{r}
data.frame(
rownames(assembleia_peixes_rm),
rownames(agua_PCs),
rownames(bacia_PCs),
rownames(estrutura_PCs),
rownames(as.matrix(dist_euclid)),
delineamento$bacia_id
)

assembleia_peixes_rm <- assembleia_peixes_rm[match(delineamento$bacia_id, rownames(assembleia_peixes_rm) ),]

data.frame(
rownames(assembleia_peixes_rm),
rownames(agua_PCs),
rownames(bacia_PCs),
rownames(estrutura_PCs),
rownames(as.matrix(dist_euclid)),
delineamento$bacia_id
)

```


### Variation Partitioning

First, lets just look at a corplot for all environmental filters.

```{r, warning=FALSE}
env_data.frame <- data.frame(est_PC1 = estrutura_PCs[,1],
                             est_PC2 = estrutura_PCs[,2],
                             #est_PC3 = estrutura_PCs[,3],
                             #est_PC4 = estrutura_PCs[,4],
                             #est_PC5 = estrutura_PCs[,5],
                             agua_PC1 = agua_PCs[,1],
                             agua_PC2 = agua_PCs[,2],
                             bacia_PC1 = bacia_PCs[,1],
                             bacia_PC2 = bacia_PCs[,2]) 

corrplot(cor(env_data.frame), type = "lower", diag = FALSE)
```

The first PCs seem all correlated with each other.



##### Now, forward selection


```{r, warning=FALSE, cache=FALSE}
est_FS <- forward_sel_manyglm(y = assembleia_peixes_rm, x = data.frame(est_PC1 = estrutura_PCs[,1],
                                                                       est_PC2 = estrutura_PCs[,2]), nBoot=999, quad = TRUE) 

agua_FS <- forward_sel_manyglm(y = assembleia_peixes_rm, x = data.frame(agua_PC1 = agua_PCs[,1],
                                                                        agua_PC2 = agua_PCs[,2]), nBoot=999, quad = TRUE) 

bacia_FS <- forward_sel_manyglm(y = assembleia_peixes_rm, x = data.frame(bacia_PC1 = bacia_PCs[,1],
                                                                         bacia_PC2 = bacia_PCs[,2]), nBoot=999, quad = TRUE) 

esp_FS <- forward_sel_manyglm(y = assembleia_peixes_rm, x = data.frame(dbmem_euclid), nBoot=999, quad = FALSE) 

```


Now, the variation partitioning

```{r, warning=FALSE}

predictors <- list(estrutura = est_FS$new_x,
                   agua = agua_FS$new_x,
                   bacia = bacia_FS$new_x,
                   urb =  data.frame(urb = urb$urb, urb_squared =  urb$urb^2),
                   esp = esp_FS$new_x)

varpart_peixes <- varpart_manyglm(resp = assembleia_peixes_rm, pred = predictors, DF_adj_r2 = FALSE)
varpart_peixes$R2_fractions_com

full_model2 <- varpart_peixes$R2_models$`estrutura-agua-bacia`
full_model2

round(varpart_peixes$R2_fractions_sp$R2_full_fraction,4)

round(varpart_peixes$R2_fractions_sp$R2_pure_fraction,4)

full_model_sp <- varpart_peixes$R2_models_sp$estrutura.agua.bacia
names(full_model_sp) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)
full_model_sp
```


Looking at fractions related to the urbanization process

```{r}
varpart_urb_est <- varpart_manyglm(resp = assembleia_peixes_rm, pred = list(estrutura = est_FS$new_x,
                                                                            urb =  data.frame(urb = urb$urb, urb_squared = 
                                                                                                urb$urb^2)), DF_adj_r2 = FALSE)

varpart_urb_est$R2_fractions_com

```


```{r}
shared_urb_estrutura <- (varpart_peixes$R2_models$estrutura + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`estrutura-urb`
shared_urb_agua <- (varpart_peixes$R2_models$agua + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`agua-urb`
shared_urb_bacia <- (varpart_peixes$R2_models$bacia + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`bacia-urb`
shared_urb_esp <- (varpart_peixes$R2_models$esp + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`urb-esp`


sp_shared_urb_estrutura <- (varpart_peixes$R2_models_sp$estrutura + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`estrutura.urb`
sp_shared_urb_agua <- (varpart_peixes$R2_models_sp$agua + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`agua.urb`
sp_shared_urb_bacia <- (varpart_peixes$R2_models_sp$bacia + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`bacia.urb`
sp_shared_urb_esp <- (varpart_peixes$R2_models_sp$esp + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`urb.esp`


estrutura_without_urb <- (varpart_peixes$R2_models$`estrutura-urb` - varpart_peixes$R2_models$urb)
agua_without_urb <- (varpart_peixes$R2_models$`agua-urb` - varpart_peixes$R2_models$urb)
bacia_without_urb <- (varpart_peixes$R2_models$`bacia-urb` - varpart_peixes$R2_models$urb)
esp_without_urb <- (varpart_peixes$R2_models$`urb-esp` - varpart_peixes$R2_models$urb)


sp_estrutura_without_urb <- (varpart_peixes$R2_models_sp$`estrutura.urb` - varpart_peixes$R2_models_sp$urb)
sp_agua_without_urb <- (varpart_peixes$R2_models_sp$`agua.urb` - varpart_peixes$R2_models_sp$urb)
sp_bacia_without_urb <- (varpart_peixes$R2_models_sp$`bacia.urb` - varpart_peixes$R2_models_sp$urb)
sp_esp_without_urb <- (varpart_peixes$R2_models_sp$`urb.esp` - varpart_peixes$R2_models_sp$urb)



urb_without_estrutura <- (varpart_peixes$R2_models$`estrutura-urb` - varpart_peixes$R2_models$estrutura)
urb_without_agua <- (varpart_peixes$R2_models$`agua-urb` - varpart_peixes$R2_models$agua)
urb_without_bacia <- (varpart_peixes$R2_models$`bacia-urb` - varpart_peixes$R2_models$bacia)
urb_without_esp <- (varpart_peixes$R2_models$`urb-esp` - varpart_peixes$R2_models$esp)


sp_urb_without_estrutura <- (varpart_peixes$R2_models_sp$`estrutura.urb` - varpart_peixes$R2_models_sp$estrutura)
sp_urb_without_agua <- (varpart_peixes$R2_models_sp$`agua.urb` - varpart_peixes$R2_models_sp$agua)
sp_urb_without_bacia <- (varpart_peixes$R2_models_sp$`bacia.urb` - varpart_peixes$R2_models_sp$bacia)
sp_urb_without_esp <- (varpart_peixes$R2_models_sp$`urb.esp` - varpart_peixes$R2_models_sp$esp)


full_urb_estrutura <- varpart_peixes$R2_models$`estrutura-urb`
full_urb_agua <- varpart_peixes$R2_models$`agua-urb`
full_urb_bacia <- varpart_peixes$R2_models$`bacia-urb`
full_urb_esp <- varpart_peixes$R2_models$`urb-esp`

sp_full_urb_estrutura <- varpart_peixes$R2_models_sp$`estrutura.urb`
sp_full_urb_agua <- varpart_peixes$R2_models_sp$`agua.urb`
sp_full_urb_bacia <- varpart_peixes$R2_models_sp$`bacia.urb`
sp_full_urb_esp <- varpart_peixes$R2_models_sp$`urb.esp`


```






Tests of significance of fractions:

```{r, warning=FALSE, cache=FALSE}
p_est <- anova(varpart_peixes$model_null,
               varpart_peixes$models$estrutura,nBoot=999)
p_est

p_bacia <- anova(varpart_peixes$model_null,
                 varpart_peixes$models$bacia,nBoot=999)
p_bacia

p_agua <- anova(varpart_peixes$model_null,
                varpart_peixes$models$agua,nBoot=999)
p_agua

p_esp <- anova(varpart_peixes$model_null,
                varpart_peixes$models$esp,nBoot=999)
p_esp

p_urb <- anova(varpart_peixes$model_null,
                varpart_peixes$models$urb,nBoot=999)
p_urb

p_est_pure <- anova(varpart_peixes$models$`agua-bacia-urb-esp`,
                    varpart_peixes$models$`estrutura-agua-bacia-urb-esp`,nBoot=999)
p_est_pure

p_bacia_pure <- anova(varpart_peixes$models$`estrutura-agua-urb-esp`,
                      varpart_peixes$models$`estrutura-agua-bacia-urb-esp`,nBoot=999)
p_bacia_pure

p_agua_pure <- anova(varpart_peixes$models$`estrutura-bacia-urb-esp`,
                     varpart_peixes$models$`estrutura-agua-bacia-urb-esp`,nBoot=999)
p_agua_pure

p_urb_pure <- anova(varpart_peixes$models$`estrutura-agua-bacia-esp`,
                     varpart_peixes$models$`estrutura-agua-bacia-urb-esp`,nBoot=999)
p_urb_pure

p_esp_pure <- anova(varpart_peixes$models$`estrutura-agua-bacia-urb`,
                     varpart_peixes$models$`estrutura-agua-bacia-urb-esp`,nBoot=999)
p_esp_pure

p_full_model <- anova(varpart_peixes$model_null,
                    varpart_peixes$models$`estrutura-agua-bacia-urb-esp`,nBoot=999)
p_full_model
```




Now, lets plot these R² values:

We will make the same procedures as before:

```{r, warning=FALSE}
names(full_model_sp) <- rownames(varpart_peixes$R2_models_sp)
ord_sp <- order(full_model_sp, decreasing = TRUE)

full_model_sp <- full_model_sp[ord_sp]

full_est <- varpart_peixes$R2_fractions_sp$R2_full_fraction$estrutura
names(full_est) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_agua <- varpart_peixes$R2_fractions_sp$R2_full_fraction$agua
names(full_agua) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_bacia <- varpart_peixes$R2_fractions_sp$R2_full_fraction$bacia
names(full_bacia) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_urb <- varpart_peixes$R2_fractions_sp$R2_full_fraction$urb
names(full_urb) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_esp <- varpart_peixes$R2_fractions_sp$R2_full_fraction$esp
names(full_esp) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)


pure_est <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$estrutura
names(pure_est) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_agua <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$agua
names(pure_agua) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_bacia <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$bacia
names(pure_bacia) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_urb <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$urb
names(pure_urb) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_esp <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$esp
names(pure_esp) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)



full_est<- full_est[ord_sp]
full_agua<- full_agua[ord_sp]
full_bacia<- full_bacia[ord_sp]
full_urb<- full_urb[ord_sp]
full_esp<- full_esp[ord_sp]


pure_est<- pure_est[ord_sp]
pure_agua<- pure_agua[ord_sp]
pure_bacia<- pure_bacia[ord_sp]
pure_urb<- pure_urb[ord_sp]
pure_esp<- pure_esp[ord_sp]

#pure_est[pure_est < 0] <- 0
#pure_agua[pure_agua < 0] <- 0
#pure_bacia[pure_bacia < 0] <- 0
#pure_urb[pure_urb < 0] <- 0
#pure_esp[pure_esp < 0] <- 0

scale_fractions <- function(full, pures){
  
  pures[pures < 0] <- 0
  
  sumed_pure <- apply(pures, MARGIN = 1, sum)
  
  scale <- full / sumed_pure
  
  scale[scale > 1] <- 1
  
  scaled_pures <- pures * scale
  
  return(scaled_pures)
}

#pure_frac_summed <- pure_est + pure_agua + pure_bacia + pure_urb + pure_esp

#scale <- full_model_sp / pure_frac_summed

#scale[scale > 1] <- 1

#pure_frac_summed_scaled <- pure_frac_summed * scale

#cbind(pure_frac_summed_scaled, full_model_sp)

#pure_est_scaled  <- pure_est * scale
#pure_agua_scaled  <- pure_agua * scale
#pure_bacia_scaled  <- pure_bacia * scale
#pure_urb_scaled  <- pure_urb * scale
#pure_esp_scaled  <- pure_esp * scale

sp_pure_frac <- data.frame(pure_est, pure_agua, pure_bacia, pure_urb, pure_esp)

sp_pure_frac_scaled <- scale_fractions(full_model_sp, sp_pure_frac)

###########


full_model <- varpart_peixes$R2_models$`estrutura-agua-bacia-urb-esp`

pure_com <- varpart_peixes$R2_fractions_com$R2_pure_fraction

pure_fracs <- varpart_peixes$R2_fractions_com$R2_pure_fraction

pure_comm_scaled <- scale_fractions(full_model, data.frame(pure_fracs))

rownames(pure_comm_scaled) <- rownames(varpart_peixes$R2_fractions_com)

```

```{r}


#Scale Estrutura

estrutura_urb_scaled <- scale_fractions(full_urb_estrutura, data.frame(estrutura_without_urb, urb_without_estrutura))
agua_urb_scaled <- scale_fractions(full_urb_agua, data.frame(agua_without_urb, urb_without_agua))
bacia_urb_scaled <- scale_fractions(full_urb_bacia, data.frame(bacia_without_urb, urb_without_bacia))
esp_urb_scaled <- scale_fractions(full_urb_esp, data.frame(esp_without_urb, urb_without_esp))

sp_estrutura_urb_scaled <- scale_fractions(sp_full_urb_estrutura, data.frame(sp_estrutura_without_urb, sp_urb_without_estrutura))
sp_agua_urb_scaled <- scale_fractions(sp_full_urb_agua, data.frame(sp_agua_without_urb, sp_urb_without_agua))
sp_bacia_urb_scaled <- scale_fractions(sp_full_urb_bacia, data.frame(sp_bacia_without_urb, sp_urb_without_bacia))
sp_esp_urb_scaled <- scale_fractions(sp_full_urb_esp, data.frame(sp_esp_without_urb, sp_urb_without_esp))

sp_estrutura_urb_scaled <- sp_estrutura_urb_scaled[ord_sp,]
sp_agua_urb_scaled <- sp_agua_urb_scaled[ord_sp,]
sp_bacia_urb_scaled <- sp_bacia_urb_scaled[ord_sp,]
sp_esp_urb_scaled <- sp_esp_urb_scaled[ord_sp,]


```


What are the percentages of the full effects of stream structure, water parameters and watershed predictores are redundant with urban cover

```{r}
estrutura_without_urb
agua_without_urb
bacia_without_urb
esp_without_urb

#Stream structure
1 - estrutura_without_urb/varpart_peixes$R2_fractions_com[1,1]

#Water parametersc
1 - agua_without_urb/varpart_peixes$R2_fractions_com[2,1]

#Watershed descriptors
1 - bacia_without_urb/varpart_peixes$R2_fractions_com[3,1]

#Spatial filters
1 - esp_without_urb/varpart_peixes$R2_fractions_com[5,1]
```


Are these fractions significant after the removal of urban cover explanation?

```{r}
p_est_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`estrutura-urb`,nBoot=999)
p_est_no_urb

p_agua_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`agua-urb`,nBoot=999)
p_agua_no_urb

p_bacia_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`bacia-urb`,nBoot=999)
p_bacia_no_urb

p_esp_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`urb-esp`,nBoot=999)
p_esp_no_urb
```




Now we can plot all of these fractions:

Pure and shared fractions fisrt:

```{r plot da particao de variancia, warning=FALSE}
#pdf("plots/varpart_pure.pdf", width = 8, height = 8, pointsize = 12)


close.screen(all.screens = TRUE)
split.screen(matrix(c(0,0.3,0.625,1,
                      0.3,1,0.625,1,
                      0,0.3,0.25,0.625,
                      0.3,1,0.25,0.625), ncol = 4, nrow = 4, byrow = TRUE))

screen(2)
par(mar = c(2,1,1,1))

fulls_urb <- rbind(full_est, full_agua, full_bacia, full_esp, full_urb)
pures_urb <- rbind(t(sp_estrutura_urb_scaled)[1,], t(sp_agua_urb_scaled)[1,],  t(sp_bacia_urb_scaled)[1,], t(sp_esp_urb_scaled)[1,], rep(0, 8))

barplot(fulls_urb, ylim = c(0,1), las = 2, col = c(darken("#98DF8A", amount = 0.25), darken("#9EDAE5", amount = 0.25), darken("#FFBB78", amount = 0.25), darken("#C49C94", amount = 0.25), "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,2), xlim = c(0,57), yaxt = "n", beside = TRUE)
par(new = TRUE)
barplot(pures_urb, ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#C49C94", "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,2), xlim = c(0,57), yaxt = "n", beside = TRUE)

box(bty = "l")
names <- colnames(fulls_urb)
names <- gsub("_"," ", names)

axis(1, at = at_generator(first = 4.5, spacing = 7, n = length(names)), gap.axis = -10, tick = TRUE, labels = FALSE, las = 2, font = 3, line = 0)

#SaD <- which(names == "Singletons and doubletons")
#axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[-SaD], gap.axis = -10, tick = TRUE, labels = names[-SaD], las = 2, font = 3, line = 0)
#axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[SaD], gap.axis = -10, tick = TRUE, labels = names[SaD], las = 2, font = 1, line = 0)

#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)
axis(2, las = 2, line = 0, labels = FALSE)
par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", xaxs = "i", yaxs = "i", )

legend(x = 99, y = 100, xjust = 1, yjust = 1, fill = c("#98DF8A", "#9EDAE5", "#FFBB78", "#C49C94", "grey30"),
       legend = c("Stream structure*", "Water parameters*", "Watershed descriptors*", "Spatial filters*", "Urban cover"), border = "transparent", bty = "n", cex = 0.9)

text(x = 65, y = 65, adj = c(0,1), labels = "*Darker colors are effects shared with", cex = 0.7)
text(x = 65, y = 61, adj = c(0,1), labels = " urban cover", cex = 0.7)



screen(1)
par(mar = c(2,4,1,1))

full_comm <- as.matrix(varpart_peixes$R2_fractions_com$R2_full_fraction[c(1,2,3,5,4)])
pure_comm <- rbind(t(estrutura_urb_scaled[1]), t(agua_urb_scaled[1]), t(bacia_urb_scaled[1]), t(esp_urb_scaled[1]), 0)


barplot(full_comm, ylim = c(0,1), las = 2, col = c(darken("#98DF8A", amount = 0.25), darken("#9EDAE5", amount = 0.25), darken("#FFBB78", amount = 0.25), darken("#C49C94", amount = 0.25), "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,1), xlim = c(0,7), yaxt = "n", beside = TRUE)
par(new = TRUE)
barplot(pure_comm, ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#C49C94", "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,1), xlim = c(0,7), yaxt = "n", beside = TRUE)

box(bty = "l")
#axis(1, at = c(2.5), gap.axis = -10, tick = FALSE, labels = "Community", las = 1, font = 1, line = -0.5)
#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)

title(ylab = "Likelihood ratio R\u00B2", cex.lab = 1.25)
axis(2, las = 2, line = 0)
letters(x = 92, y = 96, "b)", cex = 1.5)
letters(x = 7, y = 96, "a)", cex = 1.5)





screen(4)
par(mar = c(2,1,1,1))
barplot(full_model_sp, ylim = c(0,1), las = 2, border = "transparent", col = "#C7C7C7", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,12.5), yaxt = "n")
par(new = TRUE)
#pure_scaleds <- rbind(pure_est_scaled, pure_agua_scaled, pure_bacia_scaled, pure_urb_scaled, pure_esp_scaled)
pure_scaleds <- t(sp_pure_frac_scaled)
barplot(pure_scaleds, ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "grey30", "#C49C94"), border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,12.5), yaxt = "n")
box(bty = "l")
names <- colnames(pure_scaleds)
names <- gsub("_"," ", names)

SaD <- which(names == "Singletons and doubletons")
axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[-SaD], gap.axis = -10, tick = TRUE, labels = names[-SaD], las = 2, font = 3, line = 0, cex.axis = 1)
axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[SaD], gap.axis = -10, tick = TRUE, labels = names[SaD], las = 2, font = 1, line = 0, cex.axis = 1)

axis(2, las = 2, line = 0, labels = FALSE)
par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", xaxs = "i", yaxs = "i", )

legend(x = 99, y = 99, xjust = 1, yjust = 1, fill = c("#C7C7C7"),
       legend = c("Shared"), border = "transparent", bty = "n")


screen(3)
par(mar = c(2,4,1,1))
barplot(as.matrix(full_model), ylim = c(0,1), las = 2, border = "transparent", col = "#C7C7C7", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,2), yaxt = "n")
par(new = TRUE)

barplot(as.matrix(pure_comm_scaled), ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "grey30", "#C49C94"), border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,2), yaxt = "n")
box(bty = "l")
axis(1, at = c(1), gap.axis = -10, tick = FALSE, labels = "Community", las = 1, font = 1, line = -0.5)
#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)

title(ylab = "Likelihood ratio R\u00B2", cex.lab = 1.25)
axis(2, las = 2, line = 0)
letters(x = 92, y = 96, "d)", cex = 1.5)
letters(x = 7, y = 96, "c)", cex = 1.5)



#dev.off()
```


### Ploting coeffitients and predicted values

Now, we will plot coeffitients for predictors that were important to describe fish community structure. We will focus on the effects of urban cover alone, and that of significant sets of environmental descriptors, which in this case are predictors of stream structure.



```{r, warning=FALSE}
urb_coefs <- varpart_peixes$models$urb$coefficients[2,]
urb_IC_coefs <- varpart_peixes$models$urb$stderr.coefficients[2,] * qnorm(0.975)
urb_upper_coefs <- urb_coefs + urb_IC_coefs
urb_lower_coefs <- urb_coefs - urb_IC_coefs

urb_2_coefs <- varpart_peixes$models$urb$coefficients[3,]
urb_2_IC_coefs <- varpart_peixes$models$urb$stderr.coefficients[3,] * qnorm(0.975)
urb_2_upper_coefs <- urb_2_coefs + urb_2_IC_coefs
urb_2_lower_coefs <- urb_2_coefs - urb_2_IC_coefs



est_coefs <- varpart_peixes$models$estrutura$coefficients[2,]
est_IC_coefs <- varpart_peixes$models$estrutura$stderr.coefficients[2,] * qnorm(0.975)
est_upper_coefs <- est_coefs + est_IC_coefs
est_lower_coefs <- est_coefs - est_IC_coefs

est_2_coefs <- varpart_peixes$models$estrutura$coefficients[3,]
est_2_IC_coefs <- varpart_peixes$models$estrutura$stderr.coefficients[3,] * qnorm(0.975)
est_2_upper_coefs <- est_2_coefs + est_2_IC_coefs
est_2_lower_coefs <- est_2_coefs - est_2_IC_coefs



agua_coefs <- varpart_peixes$models$agua$coefficients[2,]
agua_IC_coefs <- varpart_peixes$models$agua$stderr.coefficients[2,] * qnorm(0.975)
agua_upper_coefs <- agua_coefs + agua_IC_coefs
agua_lower_coefs <- agua_coefs - agua_IC_coefs

agua_2_coefs <- varpart_peixes$models$agua$coefficients[3,]
agua_2_IC_coefs <- varpart_peixes$models$agua$stderr.coefficients[3,] * qnorm(0.975)
agua_2_upper_coefs <- agua_2_coefs + agua_2_IC_coefs
agua_2_lower_coefs <- agua_2_coefs - agua_2_IC_coefs



bacia_coefs1 <- varpart_peixes$models$bacia$coefficients[2,]
bacia_IC_coefs1 <- varpart_peixes$models$bacia$stderr.coefficients[2,] * qnorm(0.975)
bacia_upper_coefs1 <- bacia_coefs1 + bacia_IC_coefs1
bacia_lower_coefs1 <- bacia_coefs1 - bacia_IC_coefs1

bacia_2_coefs1 <- varpart_peixes$models$bacia$coefficients[3,]
bacia_2_IC_coefs1 <- varpart_peixes$models$bacia$stderr.coefficients[3,] * qnorm(0.975)
bacia_2_upper_coefs1 <- bacia_2_coefs1 + bacia_2_IC_coefs1
bacia_2_lower_coefs1 <- bacia_2_coefs1 - bacia_2_IC_coefs1



bacia_coefs2 <- varpart_peixes$models$bacia$coefficients[4,]
bacia_IC_coefs2 <- varpart_peixes$models$bacia$stderr.coefficients[4,] * qnorm(0.975)
bacia_upper_coefs2 <- bacia_coefs2 + bacia_IC_coefs2
bacia_lower_coefs2 <- bacia_coefs2 - bacia_IC_coefs2

bacia_2_coefs2 <- varpart_peixes$models$bacia$coefficients[5,]
bacia_2_IC_coefs2 <- varpart_peixes$models$bacia$stderr.coefficients[5,] * qnorm(0.975)
bacia_2_upper_coefs2 <- bacia_2_coefs2 + bacia_2_IC_coefs2
bacia_2_lower_coefs2 <- bacia_2_coefs2 - bacia_2_IC_coefs2


names <- names(urb_coefs)
names <- gsub("_"," ", names)

#pdf("plots/coefficients.pdf", width = 11, height = 8, pointsize = 12)

close.screen(all.screens = TRUE)
split.screen(matrix(c(0,0.2,0.5,1,
                      0.2,0.36,0.5,1,
                      0.36,0.52,0.5,1, 
                      0.52,0.68,0.5,1,
                      0.68,0.84,0.5,1,
                      0.84,1,0.5,1,
                      0,0.2,0,0.5,
                      0.2,0.36,0,0.5,
                      0.36,0.52,0,0.5, 
                      0.52,0.68,0,0.5,
                      0.68,0.84,0,0.5,
                      0.84,1,0,0.5), ncol = 4, nrow = 12, byrow = TRUE))

sp_font <- rep(3, length(names))
sp_font[names == "Singletons and doubletons"] <- 1

screen(1)
screen(2, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = urb_coefs, upper = urb_upper_coefs,
            lower = urb_lower_coefs, col_sig = "#AEC7E8",
            cex_sig = 1.5, species_labels = names, yaxis_font = sp_font, cex.axis = 0.9)
title(xlab = "Urban cover", cex.lab = 1, line = 2.5)
#screen(2, new = FALSE)
letters(x = 12, y = 94, "a)", cex = 1.5)

screen(3, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = est_coefs, upper = est_upper_coefs,
            lower = est_lower_coefs, col_sig = "#98DF8A",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Stream", cex.lab = 1, line = 2)
title(xlab = "structure PC1", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "b)", cex = 1.5)

screen(4, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = agua_coefs, upper = agua_upper_coefs,
            lower = agua_lower_coefs, col_sig = "#9EDAE5",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Water", cex.lab = 1, line = 2)
title(xlab = "parameters PC1", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "c)", cex = 1.5)

screen(5, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = bacia_coefs1, upper = bacia_upper_coefs1,
            lower = bacia_lower_coefs1, col_sig = "#FFBB78",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Watershed", cex.lab = 1, line = 2)
title(xlab = "descriptors PC1", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "d)", cex = 1.5)


screen(6, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = bacia_coefs2, upper = bacia_upper_coefs2,
            lower = bacia_lower_coefs2, col_sig = "#FFBB78",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Watershed", cex.lab = 1, line = 2)
title(xlab = "descriptors PC2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "e)", cex = 1.5)


screen(7)
screen(8, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = urb_2_coefs, upper = urb_2_upper_coefs,
            lower = urb_2_lower_coefs, col_sig = "#AEC7E8",
            cex_sig = 1.5, species_labels = names, yaxis_font = sp_font, cex.axis = 0.9)
title(xlab = "(Urban cover)\u00B2", cex.lab = 1, line = 2.5)
#screen(2, new = FALSE)
letters(x = 12, y = 94, "f)", cex = 1.5)

screen(9, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = est_2_coefs, upper = est_2_upper_coefs,
            lower = est_2_lower_coefs, col_sig = "#98DF8A",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "(Stream", cex.lab = 1, line = 2)
title(xlab = "structure PC1)\u00B2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "g)", cex = 1.5)


screen(10, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = agua_2_coefs, upper = agua_2_upper_coefs,
            lower = agua_2_lower_coefs, col_sig = "#9EDAE5",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "(Water", cex.lab = 1, line = 2)
title(xlab = "parameters PC1)\u00B2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "h)", cex = 1.5)

screen(11, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = bacia_2_coefs1, upper = bacia_2_upper_coefs1,
            lower = bacia_2_lower_coefs1, col_sig = "#FFBB78",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "(Watershed", cex.lab = 1, line = 2)
title(xlab = "descriptors PC1)\u00B2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "i)", cex = 1.5)

screen(12, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = bacia_2_coefs2, upper = bacia_2_upper_coefs2,
            lower = bacia_2_lower_coefs2, col_sig = "#FFBB78",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "(Watershed", cex.lab = 1, line = 2)
title(xlab = "descriptors PC2)\u00B2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "j)", cex = 1.5)



#dev.off()

```



Now, we can also plot species predictions for the models we fitted, specifically, we can plot the effects of urban cover and stream structure on fish abundances.

First, lets generate predictions:

```{r, warning=FALSE}


newdata_urb <- data.frame(urb = seq(from = min(urb), to = max(urb), length.out = 100))
newdata_urb$urb_squared <- newdata_urb$urb^2
predicted_urb <- predict.manyglm(varpart_peixes$models$urb, newdata = newdata_urb, type = "response")
scaled_ubr <- scale(delineamento$urbana)
center <- attr(scaled_ubr, "scaled:center")
scale <- attr(scaled_ubr, "scaled:scale")
urb_plot <- (newdata_urb$urb * scale) + center

names <- colnames(predicted_urb)
names <- gsub("_"," ", names)

names[names == "Poecilia reticulata"] <- "Poecilia reticulata*"
names[names == "Phalloceros reisi"] <- "Phalloceros reisi*"
names[names == "Phalloceros harpagos"] <- "Phalloceros harpagos*"


colors <- c("#8DD3C7", "#BEBADA", "#FB8072", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5","#BC80BD")

names(colors) <- names

line_bg <- c(rep("white", ncol(predicted_urb)))
line_tp <- rep(2, ncol(predicted_urb))
lwd <- rep(3, ncol(predicted_urb))


line_tp_urb <- rep(2, ncol(predicted_urb))
line_tp_urb[which(urb_IC_coefs < abs(urb_coefs))] <- 1
line_tp_urb[which(urb_2_IC_coefs < abs(urb_2_coefs))] <- 1

lwd_urb <- rep(3, ncol(predicted_urb))
lwd_urb[which(urb_IC_coefs < abs(urb_coefs))] <- 4
lwd_urb[which(urb_2_IC_coefs < abs(urb_2_coefs))] <- 4

###################################################

newdata_est <- data.frame(est_PC1 = seq(from = min(est_FS$new_x$est_PC1), to = max(est_FS$new_x$est_PC1), length.out = 100))
newdata_est$est_PC1_squared <- newdata_est$est_PC1^2
predicted_est <- predict.manyglm(varpart_peixes$models$estrutura, newdata = newdata_est, type = "response")

line_tp_est <- rep(2, ncol(predicted_est))
line_tp_est[which(est_IC_coefs < abs(est_coefs))] <- 1
line_tp_est[which(est_2_IC_coefs < abs(est_2_coefs))] <- 1

lwd_est <- rep(3, ncol(predicted_est))
lwd_est[which(est_IC_coefs < abs(est_coefs))] <- 4
lwd_est[which(est_2_IC_coefs < abs(est_2_coefs))] <- 4

###################################################

newdata_agua <- data.frame(agua_PC1 = seq(from = min(agua_FS$new_x$agua_PC1), to = max(agua_FS$new_x$agua_PC1), length.out = 100))
newdata_agua$agua_PC1_squared <- newdata_agua$agua_PC1^2
predicted_agua <- predict.manyglm(varpart_peixes$models$agua, newdata = newdata_agua, type = "response")

line_tp_agua <- rep(2, ncol(predicted_agua))
line_tp_agua[which(agua_IC_coefs < abs(agua_coefs))] <- 1
line_tp_agua[which(agua_2_IC_coefs < abs(agua_2_coefs))] <- 1

lwd_agua <- rep(3, ncol(predicted_agua))
lwd_agua[which(agua_IC_coefs < abs(agua_coefs))] <- 4
lwd_agua[which(agua_2_IC_coefs < abs(agua_2_coefs))] <- 4


###################################################

newdata_bacia1 <- data.frame(bacia_PC1 = seq(from = min(bacia_FS$new_x$bacia_PC1), to = max(bacia_FS$new_x$bacia_PC1), length.out = 100),
                            bacia_PC2 = rep(0,100))
newdata_bacia1$bacia_PC1_squared <- newdata_bacia1$bacia_PC1^2
newdata_bacia1$bacia_PC2_squared <- newdata_bacia1$bacia_PC2^2

predicted_bacia1 <- predict.manyglm(varpart_peixes$models$bacia, newdata = newdata_bacia1, type = "response")

line_tp_bacia1 <- rep(2, ncol(predicted_bacia1))
line_tp_bacia1[which(bacia_IC_coefs1 < abs(bacia_coefs1))] <- 1
line_tp_bacia1[which(bacia_2_IC_coefs1 < abs(bacia_2_coefs1))] <- 1

lwd_bacia1 <- rep(3, ncol(predicted_bacia1))
lwd_bacia1[which(bacia_IC_coefs1 < abs(bacia_coefs1))] <- 4
lwd_bacia1[which(bacia_2_IC_coefs1 < abs(bacia_2_coefs1))] <- 4

###################################################

newdata_bacia2 <- data.frame(bacia_PC1 = rep(0,100),
                            bacia_PC2 = seq(from = min(bacia_FS$new_x$bacia_PC2), to = max(bacia_FS$new_x$bacia_PC2), length.out = 100))
newdata_bacia2$bacia_PC1_squared <- newdata_bacia2$bacia_PC1^2
newdata_bacia2$bacia_PC2_squared <- newdata_bacia2$bacia_PC2^2

predicted_bacia2 <- predict.manyglm(varpart_peixes$models$bacia, newdata = newdata_bacia2, type = "response")

line_tp_bacia2 <- rep(2, ncol(predicted_bacia2))
line_tp_bacia2[which(bacia_IC_coefs2 < abs(bacia_coefs2))] <- 1
line_tp_bacia2[which(bacia_2_IC_coefs2 < abs(bacia_2_coefs2))] <- 1

lwd_bacia2 <- rep(3, ncol(predicted_bacia2))
lwd_bacia2[which(bacia_IC_coefs2 < abs(bacia_coefs2))] <- 4
lwd_bacia2[which(bacia_2_IC_coefs2 < abs(bacia_2_coefs2))] <- 4



poecilidae <- which(colnames(predicted_urb) == "Phalloceros_reisi" | colnames(predicted_urb) == "Phalloceros_harpagos" | colnames(predicted_urb) == "Poecilia_reticulata")
NOT_poecilidae <- which(colnames(predicted_urb) != "Phalloceros_reisi" & colnames(predicted_urb) != "Phalloceros_harpagos" & colnames(predicted_urb) != "Poecilia_reticulata")

```

```{r, warning=FALSE}

#pdf("plots/predictions.pdf", width = 11, height = 10, pointsize = 12)



close.screen(all.screens = TRUE)
split.screen(matrix(c(0  , 0.5, 0.6666666, 1  ,
                      0.5, 1  , 0.6666666, 1  ,
                      0  , 0.5, 0.3333333, 0.6666666,
                      0.5, 1  , 0.3333333, 0.6666666, 
                      0  , 0.5, 0, 0.3333333,
                      0.5, 1  , 0, 0.3333333), ncol = 4, nrow = 6, byrow = TRUE))


###################################################################### FIRST PLOT
screen(1)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,35), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_urb[,NOT_poecilidae])){
  lines(x = urb_plot, y = predicted_urb[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = predicted_urb[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_urb[NOT_poecilidae][i], lty = line_tp_urb[NOT_poecilidae][i])
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_urb[,poecilidae])){
  lines(x = urb_plot, y = predicted_urb[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = predicted_urb[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_urb[poecilidae][i], lty = line_tp_urb[poecilidae][i])
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

axis(1, labels = FALSE)
axis(1, labels = TRUE, tick = FALSE, line = -0.5)
title(xlab = "Urban cover (%)", line = 2)
letters(x = 5, y = 95, "a)", cex = 1.5)

###################################################################### SECOND PLOT
screen(2)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,35), xlim = c(min(newdata_est$est_PC1),max(newdata_est$est_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_est[,NOT_poecilidae])){
  lines(x = newdata_est$est_PC1, y = predicted_est[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est$est_PC1, y = predicted_est[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_est[NOT_poecilidae][i], lty = line_tp_est[NOT_poecilidae][i])
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_est$est_PC1),max(newdata_est$est_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_est[,poecilidae])){
  lines(x = newdata_est$est_PC1, y = predicted_est[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est$est_PC1, y = predicted_est[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_est[poecilidae][i], lty = line_tp_est[poecilidae][i])
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Arboreal vegetation", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_est$est_PC1)+0.4)
#mtext("waste inside and",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_est$est_PC1)+0.4)
#mtext("outside the channel",       side = 1, line = 1.5    , adj = 1, cex = 0.8, at = max(newdata_est$est_PC1)+0.4)

mtext("Anthropogenic entrenchment", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_est$est_PC1)-0.4)


title(xlab = "Stream ", line = 0.5)
title(xlab = "structure", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "b)", cex = 1.5)


###################################################################### THIRD PLOT

screen(3)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,35), xlim = c(min(newdata_agua$agua_PC1),max(newdata_agua$agua_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_agua[,NOT_poecilidae])){
  lines(x = newdata_agua$agua_PC1, y = predicted_agua[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_agua$agua_PC1, y = predicted_agua[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_agua[NOT_poecilidae][i], lty = line_tp_agua[NOT_poecilidae][i])
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_agua$agua_PC1),max(newdata_agua$agua_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_agua[,poecilidae])){
  lines(x = newdata_agua$agua_PC1, y = predicted_agua[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_agua$agua_PC1, y = predicted_agua[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_agua[poecilidae][i], lty = line_tp_agua[poecilidae][i])
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Higher temperature and pH",       side = 1, line = 0    , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)
mtext("More total dissolved C and N",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)
mtext("More chlorophyll-a", side = 1, line = 1.5 , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)
mtext("More phycocyanin",       side = 1, line = 2.25    , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)


mtext("Greater dissolved Oxigen", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_agua$agua_PC1)-0.4)
mtext("Greater redox potential", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_agua$agua_PC1)-0.4)
mtext("Lower conductivity", side = 1, line = 1.5 , adj = 0, cex = 0.8, at = min(newdata_agua$agua_PC1)-0.4)

title(xlab = "Water", line = 0.5)
title(xlab = "parameters", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "c)", cex = 1.5)





###################################################################### FOURTH PLOT


screen(4)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,35), xlim = c(min(newdata_bacia1$bacia_PC1),max(newdata_bacia1$bacia_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_bacia1[,NOT_poecilidae])){
  lines(x = newdata_bacia1$bacia_PC1, y = predicted_bacia1[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia1$bacia_PC1, y = predicted_bacia1[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_bacia1[NOT_poecilidae][i], lty = line_tp_bacia1[NOT_poecilidae][i])
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_bacia1$bacia_PC1),max(newdata_bacia1$bacia_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_bacia1[,poecilidae])){
  lines(x = newdata_bacia1$bacia_PC1, y = predicted_bacia1[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia1$bacia_PC1, y = predicted_bacia1[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_bacia1[poecilidae][i], lty = line_tp_bacia1[poecilidae][i])
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Greater forest cover", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_bacia1$bacia_PC1)+0.4)
mtext("Steeper slope",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_bacia1$bacia_PC1)+0.4)

mtext("Larger area", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_bacia1$bacia_PC1)-0.4)
mtext("Lower altitude", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_bacia1$bacia_PC1)-0.4)

title(xlab = "Watershed", line = 0.5)
title(xlab = "descriptors", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "d)", cex = 1.5)






screen(5)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,35), xlim = c(min(newdata_bacia2$bacia_PC2),max(newdata_bacia2$bacia_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_bacia2[,NOT_poecilidae])){
  lines(x = newdata_bacia2$bacia_PC2, y = predicted_bacia2[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia2$bacia_PC2, y = predicted_bacia2[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_bacia2[NOT_poecilidae][i], lty = line_tp_bacia2[NOT_poecilidae][i])
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_bacia2$bacia_PC2),max(newdata_bacia2$bacia_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_bacia2[,poecilidae])){
  lines(x = newdata_bacia2$bacia_PC2, y = predicted_bacia2[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia2$bacia_PC2, y = predicted_bacia2[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_bacia2[poecilidae][i], lty = line_tp_bacia2[poecilidae][i])
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Circular and", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_bacia2$bacia_PC2)+0.4)
mtext("compact watersheds",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_bacia2$bacia_PC2)+0.4)
mtext("Lower altitude",       side = 1, line = 1.5    , adj = 1, cex = 0.8, at = max(newdata_bacia2$bacia_PC2)+0.4)

mtext("Elongated and", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_bacia2$bacia_PC2)-0.4)
mtext("irregular watersheds", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_bacia2$bacia_PC2)-0.4)

title(xlab = "Watershed", line = 0.5)
title(xlab = "descriptors", line = 1.5)
title(xlab = "(PC2)", line = 2.5)

letters(x = 5, y = 95, "e)", cex = 1.5)




###################################################################### 
screen(6)
par(mar = c(0,0,0,0))
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", , xaxs = "i", yaxs = "i", bty = "n")

font <- rep(3, length(names))
font[which(names == "Singletons and doubletons")] <- 1

legend(x = 50, y = 50, col = colors, lty = 1, lwd = 4, legend = names, ncol = 1, xjust = 0.5, yjust = 0.5, box.lty = 0, text.font = font)

#dev.off()
  


```





It is also usefull to plot loess predictions to compare with the predictions from our models:

```{r}

degree <- 2
span <- 0.75


loess_pred_urb <- matrix(data = NA, nrow = 100, ncol = ncol(varpart_peixes$models$estrutura$y))

for(i in 1:ncol(loess_pred_urb)){
  loess <- loess(varpart_peixes$models$estrutura$y[,i] ~ urb,  span = span, data = predictors$urb, degree = degree)
  newdata_urb <- data.frame(urb = seq(from = min(predictors$urb), to = max(predictors$urb), length.out = 100))
  loess_pred_urb[,i] <- predict(loess, newdata = newdata_urb)
}

colnames(loess_pred_urb) <- colnames(varpart_peixes$models$estrutura$y)

scaled_ubr <- scale(delineamento$urbana)
center <- attr(scaled_ubr, "scaled:center")
scale <- attr(scaled_ubr, "scaled:scale")
urb_plot <- (newdata_urb$urb * scale) + center

names <- colnames(loess_pred_urb)
names <- gsub("_"," ", names)

names[names == "Poecilia reticulata"] <- "Poecilia reticulata*"
names[names == "Phalloceros reisi"] <- "Phalloceros reisi*"
names[names == "Phalloceros harpagos"] <- "Phalloceros harpagos*"


colors <- c("#8DD3C7", "#BEBADA", "#FB8072", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5","#BC80BD")

names(colors) <- names


###################################################
loess_pred_est <- matrix(data = NA, nrow = 100, ncol = ncol(varpart_peixes$models$estrutura$y))

for(i in 1:ncol(loess_pred_est)){
  loess <- loess(varpart_peixes$models$estrutura$y[,i] ~ est_PC1,  span = span, data = predictors$est, degree = degree)
  newdata_est <- data.frame(est_PC1 = seq(from = min(predictors$est$est_PC1), to = max(predictors$est$est_PC1), length.out = 100))
  loess_pred_est[,i] <- predict(loess, newdata = newdata_est)
}

colnames(loess_pred_est) <- colnames(varpart_peixes$models$estrutura$y)

est_plot <- newdata_est$est_PC1


###################################################
loess_pred_agua <- matrix(data = NA, nrow = 100, ncol = ncol(varpart_peixes$models$agua$y))

for(i in 1:ncol(loess_pred_agua)){
  loess <- loess(varpart_peixes$models$agua$y[,i] ~ agua_PC1,  span = span, data = predictors$agua, degree = degree)
  newdata_agua <- data.frame(agua_PC1 = seq(from = min(predictors$agua$agua_PC1), to = max(predictors$agua$agua_PC1), length.out = 100))
  loess_pred_agua[,i] <- predict(loess, newdata = newdata_agua)
}

colnames(loess_pred_agua) <- colnames(varpart_peixes$models$agua$y)

agua_plot <- newdata_agua$agua_PC1

###################################################
loess_pred_bacia <- matrix(data = NA, nrow = 100, ncol = ncol(varpart_peixes$models$bacia$y))

for(i in 1:ncol(loess_pred_bacia)){
  loess <- loess(varpart_peixes$models$bacia$y[,i] ~ bacia_PC1,  span = span, data = predictors$bacia, degree = degree)
  newdata_bacia <- data.frame(bacia_PC1 = seq(from = min(predictors$bacia$bacia_PC1), to = max(predictors$bacia$bacia_PC1), length.out = 100))
  loess_pred_bacia[,i] <- predict(loess, newdata = newdata_bacia)
}

colnames(loess_pred_bacia) <- colnames(varpart_peixes$models$bacia$y)

bacia_plot <- newdata_bacia$bacia_PC1



poecilidae <- which(colnames(loess_pred_urb) == "Phalloceros_reisi" | colnames(loess_pred_urb) == "Phalloceros_harpagos" | colnames(loess_pred_urb) == "Poecilia_reticulata")
NOT_poecilidae <- which(colnames(loess_pred_urb) != "Phalloceros_reisi" & colnames(loess_pred_urb) != "Phalloceros_harpagos" & colnames(loess_pred_urb) != "Poecilia_reticulata")



###################################################
loess_pred_bacia2 <- matrix(data = NA, nrow = 100, ncol = ncol(varpart_peixes$models$bacia$y))

for(i in 1:ncol(loess_pred_bacia2)){
  loess <- loess(varpart_peixes$models$bacia$y[,i] ~ bacia_PC2,  span = span, data = predictors$bacia, degree = degree)
  newdata_bacia2 <- data.frame(bacia_PC2 = seq(from = min(predictors$bacia$bacia_PC2), to = max(predictors$bacia$bacia_PC2), length.out = 100))
  loess_pred_bacia2[,i] <- predict(loess, newdata = newdata_bacia2)
}

colnames(loess_pred_bacia2) <- colnames(varpart_peixes$models$bacia$y)

bacia_plot2 <- newdata_bacia2$bacia_PC2



poecilidae <- which(colnames(loess_pred_urb) == "Phalloceros_reisi" | colnames(loess_pred_urb) == "Phalloceros_harpagos" | colnames(loess_pred_urb) == "Poecilia_reticulata")
NOT_poecilidae <- which(colnames(loess_pred_urb) != "Phalloceros_reisi" & colnames(loess_pred_urb) != "Phalloceros_harpagos" & colnames(loess_pred_urb) != "Poecilia_reticulata")


```









```{r, warning=FALSE}

#pdf("plots/predictions_loess.pdf", width = 11, height = 10, pointsize = 12)



close.screen(all.screens = TRUE)
split.screen(matrix(c(0  , 0.5, 0.6666666, 1  ,
                      0.5, 1  , 0.6666666, 1  ,
                      0  , 0.5, 0.3333333, 0.6666666,
                      0.5, 1  , 0.3333333, 0.6666666, 
                      0  , 0.5, 0, 0.3333333,
                      0.5, 1  , 0, 0.3333333), ncol = 4, nrow = 6, byrow = TRUE))


###################################################################### FIRST PLOT
screen(1)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,12), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(loess_pred_urb[,NOT_poecilidae])){
  lines(x = urb_plot, y = loess_pred_urb[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = loess_pred_urb[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = 4, lty = 1)
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,600), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(loess_pred_urb[,poecilidae])){
  lines(x = urb_plot, y = loess_pred_urb[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = loess_pred_urb[,poecilidae][,i], col = colors[poecilidae][i], lwd = 4, lty = 1)
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

axis(1, labels = FALSE)
axis(1, labels = TRUE, tick = FALSE, line = -0.5)
title(xlab = "Urban cover (%)", line = 2)
letters(x = 5, y = 95, "a)", cex = 1.5)

###################################################################### SECOND PLOT
screen(2)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,12), xlim = c(min(newdata_est$est_PC1),max(newdata_est$est_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(loess_pred_est[,NOT_poecilidae])){
  lines(x = newdata_est$est_PC1, y = loess_pred_est[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est$est_PC1, y = loess_pred_est[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = 4, lty = 1)
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,600), xlim = c(min(newdata_est$est_PC1),max(newdata_est$est_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(loess_pred_est[,poecilidae])){
  lines(x = newdata_est$est_PC1, y = loess_pred_est[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est$est_PC1, y = loess_pred_est[,poecilidae][,i], col = colors[poecilidae][i], lwd = 4, lty = 1)
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Arboreal vegetation", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_est$est_PC1)+0.4)
#mtext("waste inside and",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_est$est_PC1)+0.4)
#mtext("outside the channel",       side = 1, line = 1.5    , adj = 1, cex = 0.8, at = max(newdata_est$est_PC1)+0.4)

mtext("Anthropogenic entrenchment", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_est$est_PC1)-0.4)


title(xlab = "Stream ", line = 0.5)
title(xlab = "structure", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "b)", cex = 1.5)


###################################################################### THIRD PLOT

screen(3)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,12), xlim = c(min(newdata_agua$agua_PC1),max(newdata_agua$agua_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(loess_pred_agua[,NOT_poecilidae])){
  lines(x = newdata_agua$agua_PC1, y = loess_pred_agua[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_agua$agua_PC1, y = loess_pred_agua[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = 4, lty = 1)
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,600), xlim = c(min(newdata_agua$agua_PC1),max(newdata_agua$agua_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(loess_pred_agua[,poecilidae])){
  lines(x = newdata_agua$agua_PC1, y = loess_pred_agua[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_agua$agua_PC1, y = loess_pred_agua[,poecilidae][,i], col = colors[poecilidae][i], lwd = 4, lty = 1)
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Higher temperature and pH",       side = 1, line = 0    , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)
mtext("More total dissolved C and N",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)
mtext("More chlorophyll-a", side = 1, line = 1.5 , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)
mtext("More phycocyanin",       side = 1, line = 2.25    , adj = 1, cex = 0.8, at = max(newdata_agua$agua_PC1)+0.4)


mtext("Greater dissolved Oxigen", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_agua$agua_PC1)-0.4)
mtext("Greater redox potential", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_agua$agua_PC1)-0.4)
mtext("Lower conductivity", side = 1, line = 1.5 , adj = 0, cex = 0.8, at = min(newdata_agua$agua_PC1)-0.4)

title(xlab = "Water", line = 0.5)
title(xlab = "parameters", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "c)", cex = 1.5)





###################################################################### FOURTH PLOT


screen(4)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,12), xlim = c(min(newdata_bacia$bacia_PC1),max(newdata_bacia$bacia_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(loess_pred_bacia[,NOT_poecilidae])){
  lines(x = newdata_bacia$bacia_PC1, y = loess_pred_bacia[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia$bacia_PC1, y = loess_pred_bacia[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = 4, lty = 1)
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,600), xlim = c(min(newdata_bacia$bacia_PC1),max(newdata_bacia$bacia_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(loess_pred_bacia[,poecilidae])){
  lines(x = newdata_bacia$bacia_PC1, y = loess_pred_bacia[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia$bacia_PC1, y = loess_pred_bacia[,poecilidae][,i], col = colors[poecilidae][i], lwd = 4, lty = 1)
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Greater forest cover", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_bacia1$bacia_PC1)+0.4)
mtext("Steeper slope",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_bacia1$bacia_PC1)+0.4)

mtext("Larger area", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_bacia1$bacia_PC1)-0.4)
mtext("Lower altitude", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_bacia1$bacia_PC1)-0.4)

title(xlab = "Watershed", line = 0.5)
title(xlab = "descriptors", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "d)", cex = 1.5)





###################################################################### FIFTH PLOT


screen(5)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,12), xlim = c(min(newdata_bacia2$bacia_PC2),max(newdata_bacia2$bacia_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(loess_pred_bacia2[,NOT_poecilidae])){
  lines(x = newdata_bacia2$bacia_PC2, y = loess_pred_bacia2[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia2$bacia_PC2, y = loess_pred_bacia2[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = 4, lty = 1)
}

axis(2, labels = FALSE)
axis(2, labels = TRUE, tick = FALSE, line = -0.5)

par(new = TRUE)
plot(NA, ylim = c(0,600), xlim = c(min(newdata_bacia2$bacia_PC2),max(newdata_bacia2$bacia_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(loess_pred_bacia2[,poecilidae])){
  lines(x = newdata_bacia2$bacia_PC2, y = loess_pred_bacia2[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_bacia2$bacia_PC2, y = loess_pred_bacia2[,poecilidae][,i], col = colors[poecilidae][i], lwd = 4, lty = 1)
}

axis(4, labels = FALSE)
axis(4, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Circular and", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_bacia2$bacia_PC2)+0.4)
mtext("compact watersheds",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_bacia2$bacia_PC2)+0.4)
mtext("Lower altitude",       side = 1, line = 1.5    , adj = 1, cex = 0.8, at = max(newdata_bacia2$bacia_PC2)+0.4)

mtext("Elongated and", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_bacia2$bacia_PC2)-0.4)
mtext("irregular watersheds", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_bacia2$bacia_PC2)-0.4)

title(xlab = "Watershed", line = 0.5)
title(xlab = "descriptors", line = 1.5)
title(xlab = "(PC2)", line = 2.5)

letters(x = 5, y = 95, "e)", cex = 1.5)




###################################################################### 
screen(6)
par(mar = c(0,0,0,0))
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", , xaxs = "i", yaxs = "i", bty = "n")

font <- rep(3, length(names))
font[which(names == "Singletons and doubletons")] <- 1

legend(x = 50, y = 50, col = colors, lty = 1, lwd = 4, legend = names, ncol = 1, xjust = 0.5, yjust = 0.5, box.lty = 0, text.font = font)

#dev.off()
  


```


