---
title: "Manyglm_varpart"
author: "Rodolfo Pelinson"
date: "`r Sys.Date()`"
output: 
  github_document: 
    fig_width: 10
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE}
dir<-("C:/Users/rodol/OneDrive/repos/Urban_fish_assemblages")
```

Loading important functions and packages

```{r, warning=FALSE}
source(paste(sep = "/",dir,"functions/remove_sp.R"))
source(paste(sep = "/",dir,"functions/R2_manyglm.R"))
source(paste(sep = "/",dir,"functions/forward_sel_manyglm.R"))
source(paste(sep = "/",dir,"functions/varpart_manyglm.R"))
source(paste(sep = "/",dir,"functions/My_coefplot.R"))
source(paste(sep = "/",dir,"functions/letters.R"))
source(paste(sep = "/",dir,"functions/at_generator.R"))



library(mvabund)
library(vegan)
library(yarrr)
library(ade4)
library(adespatial)
library(corrplot)
library(colorspace)

set.seed(1)
```

# Loading data

```{r, warning=FALSE, message =FALSE}
assembleia_peixes <- read.csv(paste(sep = "/",dir,"data/com_por_bacia.csv"), row.names = 1)
water_quality_PCs <- read.csv(paste(sep = "/",dir,"data/pcas_amb/water_quality_PCs.csv"), row.names = 1)
structural_complexity_PCs <- read.csv(paste(sep = "/",dir,"data/pcas_amb/structural_complexity_PCs.csv"), row.names = 1)
hydrology_PCs <- read.csv(paste(sep = "/",dir,"data/pcas_amb/hydrology_PCs.csv"), row.names = 1)
delineamento <- read.csv(paste(sep = "/",dir,"data/delineamento.csv"))
dist_euclid <- read.csv(paste(sep = "/",dir,"data/dist/Matriz_distancia_matriz_euclidiana.csv"), row.names = 1)




```

Removing species with less than 2 presences and combining them into the artificial "Singletons and doubletons" species.

```{r, warning=FALSE, message = FALSE}
assembleia_peixes <- read.csv(paste(sep = "/",dir,"data/com_por_bacia.csv"), row.names = 1)
assembleia_peixes <- assembleia_peixes[,-c(4,11)]

ncol(assembleia_peixes)

assembleia_peixes_rm <- remove_sp(com = assembleia_peixes, n_sp = 1)

singletons_doubletons <- remove_sp(assembleia_peixes, 2, less_equal = TRUE)
doubletons <- remove_sp(singletons_doubletons, 1)

ncol(doubletons)

singletons <- remove_sp(assembleia_peixes, 1, less_equal = TRUE)

ncol(singletons)


sing_doub_ab <- rowSums(singletons_doubletons)
sing_ab <- rowSums(singletons)

sing_doub <- rowSums(decostand(singletons_doubletons, method = "pa")) 
sing <- rowSums(decostand(singletons, method = "pa")) 

assembleia_peixes_rm <- data.frame(assembleia_peixes_rm, Singletons = sing_ab)
```


```{r}

colSums(assembleia_peixes)[order(colSums(assembleia_peixes), decreasing = TRUE)]


assembleia_peixes_oc <- colSums(decostand(assembleia_peixes, method = "pa"))

assembleia_peixes_oc[order(assembleia_peixes_oc, decreasing = TRUE)]



```



Percentage of Poecilidae

```{r}

abundances <- rowSums(assembleia_peixes)
total_ind <- sum(abundances)
total_ind

abundances_poecilidae <- rowSums(assembleia_peixes[,c(3,4,9,18)])
total_ind_poecilidae <- sum(abundances_poecilidae)
total_ind_poecilidae


total_ind_poecilidae/total_ind


```



# Preparing and standardizing predictors

```{r, warning=FALSE, message = FALSE}
urb <- data.frame(urb = delineamento$urbana)

urb <- decostand(urb, method = "stand")
water_quality_PCs <- decostand(water_quality_PCs, method = "stand")
structural_complexity_PCs <- decostand(structural_complexity_PCs, method = "stand")
hydrology_PCs <- decostand(hydrology_PCs, method = "stand")
```

## Producing spatial filters

```{r, warning=FALSE}
dist_euclid <- as.dist(dist_euclid)

dbmem_euclid <- dbmem(dist_euclid, thresh = NULL, MEM.autocor = c("positive", "non-null", "all", "negative"), store.listw = TRUE, silent = FALSE)

dbmem_euclid <- decostand(dbmem_euclid, method = "stand")
```

Checking if the rows of all data frames match

```{r}
data.frame(
rownames(assembleia_peixes_rm),
rownames(water_quality_PCs),
rownames(hydrology_PCs),
rownames(structural_complexity_PCs),
rownames(as.matrix(dist_euclid)),
delineamento$bacia_id
)

assembleia_peixes_rm <- assembleia_peixes_rm[match(delineamento$bacia_id, rownames(assembleia_peixes_rm) ),]

data.frame(
rownames(assembleia_peixes_rm),
rownames(water_quality_PCs),
rownames(hydrology_PCs),
rownames(structural_complexity_PCs),
rownames(as.matrix(dist_euclid)),
delineamento$bacia_id
)

```


# Variation Partitioning

First, lets just look at a corplot for all environmental filters.

```{r, warning=FALSE}
env_data.frame <- data.frame(est_PC1 = structural_complexity_PCs[,1],
                             est_PC2 = structural_complexity_PCs[,2],
                             #est_PC3 = structural_complexity_PCs[,3],
                             #est_PC4 = structural_complexity_PCs[,4],
                             #est_PC5 = structural_complexity_PCs[,5],
                             water_quality_PC1 = water_quality_PCs[,1],
                             water_quality_PC2 = water_quality_PCs[,2],
                             #water_quality_PC3 = water_quality_PCs[,3],
                             hydrology_PC1 = hydrology_PCs[,1],
                             hydrology_PC2 = hydrology_PCs[,2])
                             #hydrology_PC3 = hydrology_PCs[,3]) 

corrplot(cor(env_data.frame), type = "lower", diag = FALSE)
```

The first PCs seem all correlated with each other.


## Quadratic effect of urban cover

```{r}
urb_pred <-  data.frame(urb = urb$urb, urb_squared =  urb$urb^2)
assembleia_peixes_rm_mv <- mvabund(assembleia_peixes_rm)

mod_null <- manyglm(assembleia_peixes_rm_mv ~ 1, data = urb_pred)
mod_lin <- manyglm(assembleia_peixes_rm_mv ~ urb, data = urb_pred)
mod_quad <- manyglm(assembleia_peixes_rm_mv ~ urb + urb_squared, data = urb_pred)

anova(mod_null, mod_lin, mod_quad, nBoot=999, show.time = "all")

```




## Forward selection


```{r, warning=FALSE, cache=TRUE}
set.seed(1); esp_FS <- forward_sel_manyglm(y = assembleia_peixes_rm, x = data.frame(dbmem_euclid), nBoot=999, quad = FALSE, adj_R2 = FALSE) 

```


## Variation partitioning

```{r, warning=FALSE}

#predictors <- list(structural_complexity = est_FS$new_x,
#                   water_quality = water_quality_FS$new_x,
#                   hydrology = hydrology_FS$new_x,
#                   urb =  data.frame(urb = urb$urb),
#                   esp = esp_FS$new_x)

structural_complexity <- data.frame(est_PC1 = structural_complexity_PCs[,1], est_PC2 = structural_complexity_PCs[,2])
water_quality <- data.frame(water_quality_PC1 = water_quality_PCs[,1], water_quality_PC2 = water_quality_PCs[,2])
hydrology <- data.frame(hydrology_PC1 = hydrology_PCs[,1], hydrology_PC2 = hydrology_PCs[,2])
urb <- data.frame(urb = urb$urb)


predictors <- list(structural_complexity = structural_complexity,
                  water_quality = water_quality,
                   hydrology = hydrology,
                   urb =  urb,
                   esp = esp_FS$new_x)

varpart_peixes <- varpart_manyglm(resp = assembleia_peixes_rm, pred = predictors, DF_adj_r2 = FALSE)
varpart_peixes$R2_fractions_com

full_model2 <- varpart_peixes$R2_models$`structural_complexity-water_quality-hydrology`
full_model2

round(varpart_peixes$R2_fractions_sp$R2_full_fraction,4)

round(varpart_peixes$R2_fractions_sp$R2_pure_fraction,4)

full_model_sp <- varpart_peixes$R2_models_sp$structural_complexity.water_quality.hydrology
names(full_model_sp) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)
full_model_sp
```


Looking at fractions related to the urbanization process

```{r}
shared_urb_structural_complexity <- (varpart_peixes$R2_models$structural_complexity + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`structural_complexity-urb`
shared_urb_water_quality <- (varpart_peixes$R2_models$water_quality + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`water_quality-urb`
shared_urb_hydrology <- (varpart_peixes$R2_models$hydrology + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`hydrology-urb`
shared_urb_esp <- (varpart_peixes$R2_models$esp + varpart_peixes$R2_models$urb) - varpart_peixes$R2_models$`urb-esp`


sp_shared_urb_structural_complexity <- (varpart_peixes$R2_models_sp$structural_complexity + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`structural_complexity.urb`
sp_shared_urb_water_quality <- (varpart_peixes$R2_models_sp$water_quality + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`water_quality.urb`
sp_shared_urb_hydrology <- (varpart_peixes$R2_models_sp$hydrology + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`hydrology.urb`
sp_shared_urb_esp <- (varpart_peixes$R2_models_sp$esp + varpart_peixes$R2_models_sp$urb) - varpart_peixes$R2_models_sp$`urb.esp`


structural_complexity_without_urb <- (varpart_peixes$R2_models$`structural_complexity-urb` - varpart_peixes$R2_models$urb)
water_quality_without_urb <- (varpart_peixes$R2_models$`water_quality-urb` - varpart_peixes$R2_models$urb)
hydrology_without_urb <- (varpart_peixes$R2_models$`hydrology-urb` - varpart_peixes$R2_models$urb)
esp_without_urb <- (varpart_peixes$R2_models$`urb-esp` - varpart_peixes$R2_models$urb)


sp_structural_complexity_without_urb <- (varpart_peixes$R2_models_sp$`structural_complexity.urb` - varpart_peixes$R2_models_sp$urb)
sp_water_quality_without_urb <- (varpart_peixes$R2_models_sp$`water_quality.urb` - varpart_peixes$R2_models_sp$urb)
sp_hydrology_without_urb <- (varpart_peixes$R2_models_sp$`hydrology.urb` - varpart_peixes$R2_models_sp$urb)
sp_esp_without_urb <- (varpart_peixes$R2_models_sp$`urb.esp` - varpart_peixes$R2_models_sp$urb)



urb_without_structural_complexity <- (varpart_peixes$R2_models$`structural_complexity-urb` - varpart_peixes$R2_models$structural_complexity)
urb_without_water_quality <- (varpart_peixes$R2_models$`water_quality-urb` - varpart_peixes$R2_models$water_quality)
urb_without_hydrology <- (varpart_peixes$R2_models$`hydrology-urb` - varpart_peixes$R2_models$hydrology)
urb_without_esp <- (varpart_peixes$R2_models$`urb-esp` - varpart_peixes$R2_models$esp)


sp_urb_without_structural_complexity <- (varpart_peixes$R2_models_sp$`structural_complexity.urb` - varpart_peixes$R2_models_sp$structural_complexity)
sp_urb_without_water_quality <- (varpart_peixes$R2_models_sp$`water_quality.urb` - varpart_peixes$R2_models_sp$water_quality)
sp_urb_without_hydrology <- (varpart_peixes$R2_models_sp$`hydrology.urb` - varpart_peixes$R2_models_sp$hydrology)
sp_urb_without_esp <- (varpart_peixes$R2_models_sp$`urb.esp` - varpart_peixes$R2_models_sp$esp)


full_urb_structural_complexity <- varpart_peixes$R2_models$`structural_complexity-urb`
full_urb_water_quality <- varpart_peixes$R2_models$`water_quality-urb`
full_urb_hydrology <- varpart_peixes$R2_models$`hydrology-urb`
full_urb_esp <- varpart_peixes$R2_models$`urb-esp`

sp_full_urb_structural_complexity <- varpart_peixes$R2_models_sp$`structural_complexity.urb`
sp_full_urb_water_quality <- varpart_peixes$R2_models_sp$`water_quality.urb`
sp_full_urb_hydrology <- varpart_peixes$R2_models_sp$`hydrology.urb`
sp_full_urb_esp <- varpart_peixes$R2_models_sp$`urb.esp`


```






## Tests of significance

```{r, warning=FALSE, cache=TRUE}
p_est <- anova(varpart_peixes$model_null,
               varpart_peixes$models$structural_complexity,nBoot=9999)
p_est

p_hydrology <- anova(varpart_peixes$model_null,
                 varpart_peixes$models$hydrology,nBoot=9999)
p_hydrology

p_water_quality <- anova(varpart_peixes$model_null,
                varpart_peixes$models$water_quality,nBoot=9999)
p_water_quality

p_esp <- anova(varpart_peixes$model_null,
                varpart_peixes$models$esp,nBoot=9999)
p_esp

p_urb <- anova(varpart_peixes$model_null,
                varpart_peixes$models$urb,nBoot=9999)
p_urb

p_est_pure <- anova(varpart_peixes$models$`water_quality-hydrology-urb-esp`,
                    varpart_peixes$models$`structural_complexity-water_quality-hydrology-urb-esp`,nBoot=9999)
p_est_pure

p_hydrology_pure <- anova(varpart_peixes$models$`structural_complexity-water_quality-urb-esp`,
                      varpart_peixes$models$`structural_complexity-water_quality-hydrology-urb-esp`,nBoot=9999)
p_hydrology_pure

p_water_quality_pure <- anova(varpart_peixes$models$`structural_complexity-hydrology-urb-esp`,
                     varpart_peixes$models$`structural_complexity-water_quality-hydrology-urb-esp`,nBoot=9999)
p_water_quality_pure

p_urb_pure <- anova(varpart_peixes$models$`structural_complexity-water_quality-hydrology-esp`,
                     varpart_peixes$models$`structural_complexity-water_quality-hydrology-urb-esp`,nBoot=9999)
p_urb_pure

p_esp_pure <- anova(varpart_peixes$models$`structural_complexity-water_quality-hydrology-urb`,
                     varpart_peixes$models$`structural_complexity-water_quality-hydrology-urb-esp`,nBoot=9999)
p_esp_pure

p_full_model <- anova(varpart_peixes$model_null,
                    varpart_peixes$models$`structural_complexity-water_quality-hydrology-urb-esp`,nBoot=9999)
p_full_model
```



## Plot of R²

Now, lets plot these R² values:

We will make the same procedures as before:

```{r, warning=FALSE}
names(full_model_sp) <- rownames(varpart_peixes$R2_models_sp)
ord_sp <- order(full_model_sp, decreasing = TRUE)

full_model_sp <- full_model_sp[ord_sp]

full_est <- varpart_peixes$R2_fractions_sp$R2_full_fraction$structural_complexity
names(full_est) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_water_quality <- varpart_peixes$R2_fractions_sp$R2_full_fraction$water_quality
names(full_water_quality) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_hydrology <- varpart_peixes$R2_fractions_sp$R2_full_fraction$hydrology
names(full_hydrology) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_urb <- varpart_peixes$R2_fractions_sp$R2_full_fraction$urb
names(full_urb) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)

full_esp <- varpart_peixes$R2_fractions_sp$R2_full_fraction$esp
names(full_esp) <- rownames(varpart_peixes$R2_fractions_sp$R2_full_fraction)


pure_est <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$structural_complexity
names(pure_est) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_water_quality <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$water_quality
names(pure_water_quality) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_hydrology <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$hydrology
names(pure_hydrology) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_urb <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$urb
names(pure_urb) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)

pure_esp <- varpart_peixes$R2_fractions_sp$R2_pure_fraction$esp
names(pure_esp) <- rownames(varpart_peixes$R2_fractions_sp$R2_pure_fraction)



full_est<- full_est[ord_sp]
full_water_quality<- full_water_quality[ord_sp]
full_hydrology<- full_hydrology[ord_sp]
full_urb<- full_urb[ord_sp]
full_esp<- full_esp[ord_sp]


pure_est<- pure_est[ord_sp]
pure_water_quality<- pure_water_quality[ord_sp]
pure_hydrology<- pure_hydrology[ord_sp]
pure_urb<- pure_urb[ord_sp]
pure_esp<- pure_esp[ord_sp]

#pure_est[pure_est < 0] <- 0
#pure_water_quality[pure_water_quality < 0] <- 0
#pure_hydrology[pure_hydrology < 0] <- 0
#pure_urb[pure_urb < 0] <- 0
#pure_esp[pure_esp < 0] <- 0

scale_fractions <- function(full, pures){
  
  pures[pures < 0] <- 0
  
  sumed_pure <- apply(pures, MARGIN = 1, sum)
  
  scale <- full / sumed_pure
  
  scale[scale > 1] <- 1
  
  scaled_pures <- pures * scale
  
  return(scaled_pures)
}

#pure_frac_summed <- pure_est + pure_water_quality + pure_hydrology + pure_urb + pure_esp

#scale <- full_model_sp / pure_frac_summed

#scale[scale > 1] <- 1

#pure_frac_summed_scaled <- pure_frac_summed * scale

#cbind(pure_frac_summed_scaled, full_model_sp)

#pure_est_scaled  <- pure_est * scale
#pure_water_quality_scaled  <- pure_water_quality * scale
#pure_hydrology_scaled  <- pure_hydrology * scale
#pure_urb_scaled  <- pure_urb * scale
#pure_esp_scaled  <- pure_esp * scale

sp_pure_frac <- data.frame(pure_est, pure_water_quality, pure_hydrology, pure_urb, pure_esp)

sp_pure_frac_scaled <- scale_fractions(full_model_sp, sp_pure_frac)

###########


full_model <- varpart_peixes$R2_models$`structural_complexity-water_quality-hydrology-urb-esp`

pure_com <- varpart_peixes$R2_fractions_com$R2_pure_fraction

pure_fracs <- varpart_peixes$R2_fractions_com$R2_pure_fraction

pure_comm_scaled <- scale_fractions(full_model, data.frame(pure_fracs))

rownames(pure_comm_scaled) <- rownames(varpart_peixes$R2_fractions_com)

```

```{r}


#Scale structural_complexity

structural_complexity_urb_scaled <- scale_fractions(full_urb_structural_complexity, data.frame(structural_complexity_without_urb, urb_without_structural_complexity))
water_quality_urb_scaled <- scale_fractions(full_urb_water_quality, data.frame(water_quality_without_urb, urb_without_water_quality))
hydrology_urb_scaled <- scale_fractions(full_urb_hydrology, data.frame(hydrology_without_urb, urb_without_hydrology))
esp_urb_scaled <- scale_fractions(full_urb_esp, data.frame(esp_without_urb, urb_without_esp))

sp_structural_complexity_urb_scaled <- scale_fractions(sp_full_urb_structural_complexity, data.frame(sp_structural_complexity_without_urb, sp_urb_without_structural_complexity))
sp_water_quality_urb_scaled <- scale_fractions(sp_full_urb_water_quality, data.frame(sp_water_quality_without_urb, sp_urb_without_water_quality))
sp_hydrology_urb_scaled <- scale_fractions(sp_full_urb_hydrology, data.frame(sp_hydrology_without_urb, sp_urb_without_hydrology))
sp_esp_urb_scaled <- scale_fractions(sp_full_urb_esp, data.frame(sp_esp_without_urb, sp_urb_without_esp))

sp_structural_complexity_urb_scaled <- sp_structural_complexity_urb_scaled[ord_sp,]
sp_water_quality_urb_scaled <- sp_water_quality_urb_scaled[ord_sp,]
sp_hydrology_urb_scaled <- sp_hydrology_urb_scaled[ord_sp,]
sp_esp_urb_scaled <- sp_esp_urb_scaled[ord_sp,]


```


What are the percentages of the full effects of stream structure, water parameters and watershed predictores are redundant with urban cover

```{r}
structural_complexity_without_urb
water_quality_without_urb
hydrology_without_urb
esp_without_urb

#Stream structure
1 - structural_complexity_without_urb/varpart_peixes$R2_fractions_com[1,1]

#Water parametersc
1 - water_quality_without_urb/varpart_peixes$R2_fractions_com[2,1]

#Watershed descriptors
1 - hydrology_without_urb/varpart_peixes$R2_fractions_com[3,1]

#Spatial filters
1 - esp_without_urb/varpart_peixes$R2_fractions_com[5,1]
```


Are these fractions significant after the removal of urban cover explanation?

```{r, cache = TRUE}
p_est_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`structural_complexity-urb`,nBoot=9999)
p_est_no_urb

p_water_quality_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`water_quality-urb`,nBoot=9999)
p_water_quality_no_urb

p_hydrology_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`hydrology-urb`,nBoot=9999)
p_hydrology_no_urb

p_esp_no_urb <- anova(varpart_peixes$models$urb,
               varpart_peixes$models$`urb-esp`,nBoot=9999)
p_esp_no_urb
```




Now we can plot all of these fractions:

Pure and shared fractions fisrt:

```{r,   fig.width = 8, fig.height = 8, dpi = 600, dev.args= list(pointsize=13)}
#svg("plots/varpart_pure.svg", width = 8, height = 8, pointsize = 13)


close.screen(all.screens = TRUE)
split.screen(matrix(c(0,0.3,0.625,1,
                      0.3,1,0.625,1,
                      0,0.3,0.25,0.625,
                      0.3,1,0.25,0.625), ncol = 4, nrow = 4, byrow = TRUE))

screen(2)
par(mar = c(2,1,1,1))

fulls_urb <- rbind(full_est, full_water_quality, full_hydrology, full_esp, full_urb)
pures_urb <- rbind(t(sp_structural_complexity_urb_scaled)[1,], t(sp_water_quality_urb_scaled)[1,],  t(sp_hydrology_urb_scaled)[1,], t(sp_esp_urb_scaled)[1,], rep(0, 8))

barplot(fulls_urb, ylim = c(0,1), las = 2, col = c(darken("#98DF8A", amount = 0.25), darken("#9EDAE5", amount = 0.25), darken("#FFBB78", amount = 0.25), darken("#C49C94", amount = 0.25), "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,2), xlim = c(0,93), yaxt = "n", beside = TRUE)
par(new = TRUE)
barplot(pures_urb, ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#C49C94", "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,2), xlim = c(0,93), yaxt = "n", beside = TRUE)

box(bty = "l")
names <- colnames(fulls_urb)
names <- gsub("_"," ", names)

axis(1, at = at_generator(first = 4.5, spacing = 7, n = length(names)), gap.axis = -10, tick = TRUE, labels = FALSE, las = 2, font = 3, line = 0)

#SaD <- which(names == "Singletons and doubletons")
#axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[-SaD], gap.axis = -10, tick = TRUE, labels = names[-SaD], las = 2, font = 3, line = 0)
#axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[SaD], gap.axis = -10, tick = TRUE, labels = names[SaD], las = 2, font = 1, line = 0)

#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)
axis(2, las = 2, line = 0, labels = FALSE)
par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", xaxs = "i", yaxs = "i", )

legend(x = 5, y = 100, xjust = 0, yjust = 1, fill = c("#98DF8A", "#9EDAE5", "#FFBB78", "#C49C94", "grey30"),
       legend = c("Structural complexity*", "Water quality*", "Hydrology*", "Spatial filters*", "Urban cover"), border = "transparent", bty = "n", cex = 0.8, ncol = 3)

text(x = 72, y = 88, adj = c(0,1), labels = "*Darker colors are effects", cex = 0.7)
text(x = 72, y = 84, adj = c(0,1), labels = "shared with urban cover", cex = 0.7)



screen(1)
par(mar = c(2,4,1,1))

full_comm <- as.matrix(varpart_peixes$R2_fractions_com$R2_full_fraction[c(1,2,3,5,4)])
pure_comm <- rbind(t(structural_complexity_urb_scaled[1]), t(water_quality_urb_scaled[1]), t(hydrology_urb_scaled[1]), t(esp_urb_scaled[1]), 0)


barplot(full_comm, ylim = c(0,1), las = 2, col = c(darken("#98DF8A", amount = 0.25), darken("#9EDAE5", amount = 0.25), darken("#FFBB78", amount = 0.25), darken("#C49C94", amount = 0.25), "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,1), xlim = c(0,7), yaxt = "n", beside = TRUE)
par(new = TRUE)
barplot(pure_comm, ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#C49C94", "grey30"),
        border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,1), xlim = c(0,7), yaxt = "n", beside = TRUE)

box(bty = "l")
#axis(1, at = c(2.5), gap.axis = -10, tick = FALSE, labels = "Community", las = 1, font = 1, line = -0.5)
#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)

title(ylab = "Likelihood ratio R\u00B2", cex.lab = 1.25)
axis(2, las = 2, line = 0)
letters(x = 92, y = 96, "b)", cex = 1.5)
letters(x = 7, y = 96, "a)", cex = 1.5)





screen(4)
par(mar = c(2,1,1,1))
barplot(full_model_sp, ylim = c(0,1), las = 2, border = "transparent", col = "#C7C7C7", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,20), yaxt = "n")
par(new = TRUE)
#pure_scaleds <- rbind(pure_est_scaled, pure_water_quality_scaled, pure_hydrology_scaled, pure_urb_scaled, pure_esp_scaled)
pure_scaleds <- t(sp_pure_frac_scaled)
barplot(pure_scaleds, ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "grey30", "#C49C94"), border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,20), yaxt = "n")
box(bty = "l")
names <- colnames(pure_scaleds)
names <- gsub("_"," ", names)

SaD <- which(names == "Singletons")
axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[-SaD], gap.axis = -10, tick = TRUE, labels = names[-SaD], las = 2, font = 3, line = 0, cex.axis = 1)
axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names))[SaD], gap.axis = -10, tick = TRUE, labels = names[SaD], las = 2, font = 1, line = 0, cex.axis = 1)

axis(2, las = 2, line = 0, labels = FALSE)
par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", xaxs = "i", yaxs = "i", )

legend(x = 99, y = 99, xjust = 1, yjust = 1, fill = c("#C7C7C7"),
       legend = c("Shared"), border = "transparent", bty = "n")


screen(3)
par(mar = c(2,4,1,1))
barplot(as.matrix(full_model), ylim = c(0,1), las = 2, border = "transparent", col = "#C7C7C7", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,2), yaxt = "n")
par(new = TRUE)

barplot(as.matrix(pure_comm_scaled), ylim = c(0,1), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "grey30", "#C49C94"), border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,2), yaxt = "n")
box(bty = "l")
axis(1, at = c(1), gap.axis = -10, tick = FALSE, labels = "Community", las = 1, font = 1, line = -0.5)
#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)

title(ylab = "Likelihood ratio R\u00B2", cex.lab = 1.25)
axis(2, las = 2, line = 0)
letters(x = 92, y = 96, "d)", cex = 1.5)
letters(x = 7, y = 96, "c)", cex = 1.5)



#dev.off()
```


# Full and partial model coefficients


```{r}
urb_coefs <- varpart_peixes$models$urb$coefficients[2,]
urb_IC_coefs <- varpart_peixes$models$urb$stderr.coefficients[2,] * qnorm(0.975)
urb_upper_coefs <- urb_coefs + urb_IC_coefs
urb_lower_coefs <- urb_coefs - urb_IC_coefs

#urb_2_coefs <- varpart_peixes$models$urb$coefficients[3,]
#urb_2_IC_coefs <- varpart_peixes$models$urb$stderr.coefficients[3,] * qnorm(0.975)
#urb_2_upper_coefs <- urb_2_coefs + urb_2_IC_coefs
#urb_2_lower_coefs <- urb_2_coefs - urb_2_IC_coefs



est_coefs <- varpart_peixes$models$structural_complexity$coefficients[2,]
est_IC_coefs <- varpart_peixes$models$structural_complexity$stderr.coefficients[2,] * qnorm(0.975)
est_upper_coefs <- est_coefs + est_IC_coefs
est_lower_coefs <- est_coefs - est_IC_coefs

est_2_coefs <- varpart_peixes$models$structural_complexity$coefficients[3,]
est_2_IC_coefs <- varpart_peixes$models$structural_complexity$stderr.coefficients[3,] * qnorm(0.975)
est_2_upper_coefs <- est_2_coefs + est_2_IC_coefs
est_2_lower_coefs <- est_2_coefs - est_2_IC_coefs



water_quality_coefs <- varpart_peixes$models$water_quality$coefficients[2,]
water_quality_IC_coefs <- varpart_peixes$models$water_quality$stderr.coefficients[2,] * qnorm(0.975)
water_quality_upper_coefs <- water_quality_coefs + water_quality_IC_coefs
water_quality_lower_coefs <- water_quality_coefs - water_quality_IC_coefs

water_quality_2_coefs <- varpart_peixes$models$water_quality$coefficients[3,]
water_quality_2_IC_coefs <- varpart_peixes$models$water_quality$stderr.coefficients[3,] * qnorm(0.975)
water_quality_2_upper_coefs <- water_quality_2_coefs + water_quality_2_IC_coefs
water_quality_2_lower_coefs <- water_quality_2_coefs - water_quality_2_IC_coefs



hydrology_coefs <- varpart_peixes$models$hydrology$coefficients[2,]
hydrology_IC_coefs <- varpart_peixes$models$hydrology$stderr.coefficients[2,] * qnorm(0.975)
hydrology_upper_coefs <- hydrology_coefs + hydrology_IC_coefs
hydrology_lower_coefs <- hydrology_coefs - hydrology_IC_coefs

hydrology_2_coefs <- varpart_peixes$models$hydrology$coefficients[3,]
hydrology_2_IC_coefs <- varpart_peixes$models$hydrology$stderr.coefficients[3,] * qnorm(0.975)
hydrology_2_upper_coefs <- hydrology_2_coefs + hydrology_2_IC_coefs
hydrology_2_lower_coefs <- hydrology_2_coefs - hydrology_2_IC_coefs


```


```{r,  warning= FALSE, fig.width = 8, fig.height = 6, dpi = 600, dev.args= list(pointsize=7)}



names <- names(urb_coefs)
names <- gsub("_"," ", names)

#svg("plots/coefficients.svg", width = 11, height = 8, pointsize = 13)

close.screen(all.screens = TRUE)
split.screen(matrix(c(0,0.15,0,1,
                      0.15,0.2714286,0,1,
                      0.2714286,0.3928572,0,1,
                      0.3928572,0.5142858,0,1,
                      0.5142858,0.6357144,0,1,
                      0.6357144,0.757143,0,1,
                      0.757143,0.8785716,0,1,
                      0.8785716,1,0,1
                      
                      #0,0.15,0,0.5,
                      #0.15,0.2714286,0,0.5,
                      #0.2714286,0.3928572,0,0.5,
                      #0.3928572,0.5142858,0,0.5,
                      #0.5142858,0.6357144,0,0.5,
                      #0.6357144,0.757143,0,0.5,
                      #0.757143,0.8785716,0,0.5,
                      #0.8785716,1,0,0.5
                      ), ncol = 4, nrow = 16, byrow = TRUE))

sp_font <- rep(3, length(names))
sp_font[names == "Singletons and doubletons"] <- 1

#screen(1)
screen(2, new = TRUE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = urb_coefs, upper = urb_upper_coefs,
            lower = urb_lower_coefs, col_sig = "#AEC7E8",
            cex_sig = 1.5, species_labels = names, yaxis_font = sp_font, cex.axis = 0.9, xlim = c(-40,10), at.xaxis = c(-40, -20, 0))
title(xlab = "Urban cover", cex.lab = 1, line = 2.5)
#screen(2, new = FALSE)
letters(x = 12, y = 94, "a)", cex = 1.5)

screen(3, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = est_coefs, upper = est_upper_coefs,
            lower = est_lower_coefs, col_sig = "#98DF8A",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Structural", cex.lab = 1, line = 2)
title(xlab = "complexity PC1", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "b)", cex = 1.5)


screen(4, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = est_2_coefs, upper = est_2_upper_coefs,
            lower = est_2_lower_coefs, col_sig = "#98DF8A",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Structural", cex.lab = 1, line = 2)
title(xlab = "complexity PC2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "c)", cex = 1.5)



screen(5, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = water_quality_coefs, upper = water_quality_upper_coefs,
            lower = water_quality_lower_coefs, col_sig = "#9EDAE5",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3, at.xaxis = c(-30, -20, -10, 0, 10))
title(xlab = "Water", cex.lab = 1, line = 2)
title(xlab = "quality PC1", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "d)", cex = 1.5)

screen(6, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = water_quality_2_coefs, upper = water_quality_2_upper_coefs,
            lower = water_quality_2_lower_coefs, col_sig = "#9EDAE5",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Water", cex.lab = 1, line = 2)
title(xlab = "quality PC2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "e)", cex = 1.5)


screen(7, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = hydrology_coefs, upper = hydrology_upper_coefs,
            lower = hydrology_lower_coefs, col_sig = "#FFBB78",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Hydrology", cex.lab = 1, line = 2)
title(xlab = "PC1", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "f)", cex = 1.5)


screen(8, new = FALSE)
par(mar = c(4,2,2,0.1))
My_coefplot(mles = hydrology_2_coefs, upper = hydrology_2_upper_coefs,
            lower = hydrology_2_lower_coefs, col_sig = "#FFBB78",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = 3)
title(xlab = "Hydrology", cex.lab = 1, line = 2)
title(xlab = "PC2", cex.lab = 1, line = 3)
letters(x = 12, y = 94, "g)", cex = 1.5)




###################################################################################################
###################################################################################################


#dev.off()

```




# Plot urban cover predictons and loess

## Predicted

```{r}

newdata_urb <- data.frame(urb = seq(from = min(urb), to = max(urb), length.out = 100))
newdata_urb$urb_squared <- newdata_urb$urb^2
predicted_urb <- predict.manyglm(varpart_peixes$models$urb, newdata = newdata_urb, type = "response")
scaled_ubr <- scale(delineamento$urbana)
center <- attr(scaled_ubr, "scaled:center")
scale <- attr(scaled_ubr, "scaled:scale")
urb_plot <- (newdata_urb$urb * scale) + center

urb_plot_pt <- ((urb * scale) + center)[,1]


names <- colnames(predicted_urb)
names <- gsub("_"," ", names)

names[names == "Poecilia reticulata"] <- "Poecilia reticulata*"
names[names == "Phalloceros reisi"] <- "Phalloceros reisi*"
names[names == "Phalloceros harpagos"] <- "Phalloceros harpagos*"
names[names == "Phalloceros vivipara"] <- "Phalloceros vivipara*"


colors <- c("#8DD3C7", "#BEBADA", "#FB8072", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5","#BC80BD", darken("#FB8072", 0.5), darken("#FDB462", 0.5), darken("#80B1D3", 0.5), darken("#B3DE69", 0.5), darken("#FCCDE5", 0.5))

names(colors) <- names

line_bg <- c(rep("white", ncol(predicted_urb)))
line_tp <- rep(3, ncol(predicted_urb))
lwd <- rep(3, ncol(predicted_urb))


line_tp_urb <- rep(5, ncol(predicted_urb))
line_tp_urb[which(urb_lower_coefs > 0 )] <- 1
line_tp_urb[which(urb_upper_coefs < 0 )] <- 1

lwd_urb <- rep(3, ncol(predicted_urb))
lwd_urb[which(urb_lower_coefs > 0 )] <- 4
lwd_urb[which(urb_upper_coefs < 0 )] <- 4



poecilidae <- which(colnames(predicted_urb) == "Phalloceros_reisi" | colnames(predicted_urb) == "Phalloceros_harpagos" | colnames(predicted_urb) == "Poecilia_reticulata" | colnames(predicted_urb) == "Poecilia_vivipara")
NOT_poecilidae <- which(colnames(predicted_urb) != "Phalloceros_reisi" & colnames(predicted_urb) != "Phalloceros_harpagos" & colnames(predicted_urb) != "Poecilia_reticulata" & colnames(predicted_urb) != "Poecilia_vivipara")

```

## Loess

```{r}
degree <- 0
span <- 0.2


loess_pred_urb <- matrix(data = NA, nrow = 100, ncol = ncol(varpart_peixes$models$structural_complexity$y))

for(i in 1:ncol(loess_pred_urb)){
  loess <- loess(varpart_peixes$models$structural_complexity$y[,i] ~ urb,  span = span, data = predictors$urb, degree = degree)
  newdata_urb <- data.frame(urb = seq(from = min(predictors$urb), to = max(predictors$urb), length.out = 100))
  loess_pred_urb[,i] <- predict(loess, newdata = newdata_urb)
}

colnames(loess_pred_urb) <- colnames(varpart_peixes$models$structural_complexity$y)

scaled_ubr <- scale(delineamento$urbana)
center <- attr(scaled_ubr, "scaled:center")
scale <- attr(scaled_ubr, "scaled:scale")
urb_plot <- (newdata_urb$urb * scale) + center

names <- colnames(loess_pred_urb)
names <- gsub("_"," ", names)

names[names == "Poecilia reticulata"] <- "Poecilia reticulata*"
names[names == "Phalloceros reisi"] <- "Phalloceros reisi*"
names[names == "Phalloceros harpagos"] <- "Phalloceros harpagos*"
names[names == "Poecilia vivipara"] <- "Poecilia vivipara*"



colors <- c("#8DD3C7", "#BEBADA", "#FB8072", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5","#BC80BD", darken("#FB8072", 0.5), darken("#FDB462", 0.5), darken("#80B1D3", 0.5), darken("#B3DE69", 0.5), darken("#FCCDE5", 0.5))

names(colors) <- names



```




```{r,   fig.width = 6, fig.height = 3.5, dpi = 600, dev.args= list(pointsize=8)}
# left, right, bottom, and top
points <- TRUE
lines <- TRUE



close.screen(all.screens = TRUE)
split.screen(matrix(c(0  , 0.7, 0, 1,
                      0.7, 1  , 0, 1), ncol = 4, nrow = 3, byrow = TRUE))


###################################################################### FIRST PLOT
screen(1)

#par(gap.axis= -10)


ymax2 <- 22
ymax3 <- 1000

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,ymax2), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_urb[,NOT_poecilidae])){
  lines(x = urb_plot, y = predicted_urb[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = predicted_urb[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_urb[NOT_poecilidae][i], lty = line_tp_urb[NOT_poecilidae][i])
  
}

if(isTRUE(points)){
  for(i in 1:ncol(loess_pred_urb[,NOT_poecilidae])){
  
  y <- assembleia_peixes_rm[,NOT_poecilidae][,i]
  y_zeros <- y == 0
  y_non_zeros <- y != 0
  
  points(x =  urb_plot_pt[y_non_zeros],y = y[y_non_zeros], pch = 21, col = "white", bg = colors[NOT_poecilidae][i], cex = 1.25)
  }
}

axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,ymax3), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_urb[,poecilidae])){
  lines(x = urb_plot, y = predicted_urb[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = predicted_urb[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_urb[poecilidae][i], lty = line_tp_urb[poecilidae][i])
}


if(isTRUE(points)){
  for(i in 1:ncol(loess_pred_urb[,poecilidae])){
  y <- assembleia_peixes_rm[,poecilidae][,i]
  y_zeros <- y == 0
  y_non_zeros <- y != 0
  
  #y[y > 300] <- y[y > 300] - 300

  points(x =  urb_plot_pt[y_non_zeros],y = y[y_non_zeros], pch = 21, col = "white", bg = colors[poecilidae][i], cex = 1.25)
}
}

axis(4, labels = FALSE, gap.axis= -10, at = c(0, 200, 400, 600, 800, 1000))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10, at = c(0, 200, 400, 600, 800, 1000))

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

axis(1, labels = FALSE)
axis(1, labels = TRUE, tick = FALSE, line = -0.5)
title(xlab = "Urban cover (%)", line = 2)
#letters(x = 5, y = 95, "a)", cex = 1.5)



screen(2)
par(mar = c(0,0,0,0))
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", , xaxs = "i", yaxs = "i", bty = "n")

font <- rep(3, length(names))
font[which(names == "Singletons")] <- 1

legend(x = 20, y = 50, col = colors, lty = 1, lwd = 4, legend = names, ncol = 1, xjust = 0.5, yjust = 0.5, box.lty = 0, text.font = font, y.intersp	= 1.5, text.width = 20)


```






```{r,   fig.width = 6, fig.height = 3.5, dpi = 600, dev.args= list(pointsize=8)}
# left, right, bottom, and top
points <- TRUE
lines <- TRUE


close.screen(all.screens = TRUE)
split.screen(matrix(c(0  , 0.7, 0, 1,
                      0.7, 1  , 0, 1), ncol = 4, nrow = 3, byrow = TRUE))


###################################################################### FIRST PLOT
screen(1)

ymax2 <- 22
ymax3 <- 1000

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,ymax2), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

if(isTRUE(lines)){
  for(i in 1:ncol(loess_pred_urb[,NOT_poecilidae])){
  lines(x = urb_plot, y = loess_pred_urb[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = loess_pred_urb[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = 4, lty = 1)
}
}


if(isTRUE(points)){
  for(i in 1:ncol(loess_pred_urb[,NOT_poecilidae])){
  
  y <- assembleia_peixes_rm[,NOT_poecilidae][,i]
  y_zeros <- y == 0
  y_non_zeros <- y != 0

  points(x =  urb_plot_pt[y_non_zeros],y = y[y_non_zeros], pch = 21, col = "white", bg = colors[NOT_poecilidae][i], cex = 1.25)
}
  

}


axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,ymax3), xlim = c(0,100), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

if(isTRUE(lines)){
  for(i in 1:ncol(loess_pred_urb[,poecilidae])){

  lines(x = urb_plot, y = loess_pred_urb[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = urb_plot, y = loess_pred_urb[,poecilidae][,i], col = colors[poecilidae][i], lwd = 4, lty = 1)
}
}


if(isTRUE(points)){
  for(i in 1:ncol(loess_pred_urb[,poecilidae])){
  y <- assembleia_peixes_rm[,poecilidae][,i]
  y_zeros <- y == 0
  y_non_zeros <- y != 0

  points(x =  urb_plot_pt[y_non_zeros],y = y[y_non_zeros], pch = 21, col = "white", bg = colors[poecilidae][i], cex = 1.25)
}

}

axis(4, labels = FALSE, gap.axis= -10, at = c(0, 200, 400, 600, 800, 1000))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10, at = c(0, 200, 400, 600, 800, 1000))

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

axis(1, labels = FALSE)
axis(1, labels = TRUE, tick = FALSE, line = -0.5)
title(xlab = "Urban cover (%)", line = 2)
#letters(x = 5, y = 95, "b)", cex = 1.5)




screen(2)
par(mar = c(0,0,0,0))
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", , xaxs = "i", yaxs = "i", bty = "n")

font <- rep(3, length(names))
font[which(names == "Singletons")] <- 1

legend(x = 20, y = 50, col = colors, lty = 1, lwd = 4, legend = names, ncol = 1, xjust = 0.5, yjust = 0.5, box.lty = 0, text.font = font, y.intersp	= 1.5, text.width = 20)


```















#Plot environmental predictions

## Full environmental predictions

Now, we can also plot species predictions for the models we fitted, specifically, we can plot the effects of urban cover and stream structure on fish abundances.

First, lets generate predictions:

```{r, warning=FALSE}

names <- colnames(assembleia_peixes_rm)
names <- gsub("_"," ", names)

names[names == "Poecilia reticulata"] <- "Poecilia reticulata*"
names[names == "Phalloceros reisi"] <- "Phalloceros reisi*"
names[names == "Phalloceros harpagos"] <- "Phalloceros harpagos*"
names[names == "Phalloceros vivipara"] <- "Phalloceros vivipara*"


colors <- c("#8DD3C7", "#BEBADA", "#FB8072", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5","#BC80BD", darken("#FB8072", 0.5), darken("#FDB462", 0.5), darken("#80B1D3", 0.5), darken("#B3DE69", 0.5), darken("#FCCDE5", 0.5))



###################################################

newdata_est1 <- data.frame(est_PC1 = seq(from = min(predictors$structural_complexity$est_PC1), to = max(predictors$structural_complexity$est_PC1), length.out = 100),
                          est_PC2 = rep(median(predictors$structural_complexity$est_PC2),100))
predicted_est1 <- predict.manyglm(varpart_peixes$models$structural_complexity, newdata = newdata_est1, type = "response")

line_tp_est1 <- rep(5, ncol(predicted_est1))
line_tp_est1[which(est_lower_coefs > 0 )] <- 1
line_tp_est1[which(est_upper_coefs < 0 )] <- 1

lwd_est1 <- rep(3, ncol(predicted_est1))
lwd_est1[which(est_lower_coefs > 0)] <- 4
lwd_est1[which(est_upper_coefs < 0 )] <- 4

###################################################

newdata_est2 <- data.frame(est_PC2 = seq(from = min(predictors$structural_complexity$est_PC2), to = max(predictors$structural_complexity$est_PC2), length.out = 100),
                          est_PC1 = rep(median(predictors$structural_complexity$est_PC1),100))
predicted_est2 <- predict.manyglm(varpart_peixes$models$structural_complexity, newdata = newdata_est2, type = "response")

line_tp_est2 <- rep(5, ncol(predicted_est2))
line_tp_est2[which(est_2_lower_coefs > 0 )] <- 1
line_tp_est2[which(est_2_upper_coefs < 0 )] <- 1

lwd_est2 <- rep(3, ncol(predicted_est2))
lwd_est2[which(est_2_lower_coefs > 0)] <- 4
lwd_est2[which(est_2_upper_coefs < 0 )] <- 4

###################################################


###################################################

newdata_water_quality1 <- data.frame(water_quality_PC1 = seq(from = min(predictors$water_quality$water_quality_PC1), to = max(predictors$water_quality$water_quality_PC1), length.out = 100),
                           water_quality_PC2 = rep(median(predictors$water_quality$water_quality_PC2),100))
predicted_water_quality1 <- predict.manyglm(varpart_peixes$models$water_quality, newdata = newdata_water_quality1, type = "response")

line_tp_water_quality1 <- rep(5, ncol(predicted_water_quality1))
line_tp_water_quality1[which(water_quality_lower_coefs > 0)] <- 1
line_tp_water_quality1[which(water_quality_upper_coefs < 0)] <- 1

lwd_water_quality1 <- rep(3, ncol(predicted_water_quality1))
lwd_water_quality1[which(water_quality_lower_coefs > 0)] <- 4
lwd_water_quality1[which(water_quality_upper_coefs < 0)] <- 4

###################################################

newdata_water_quality2 <- data.frame(water_quality_PC2 = seq(from = min(predictors$water_quality$water_quality_PC2), to = max(predictors$water_quality$water_quality_PC2), length.out = 100),
                           water_quality_PC1 = rep(median(predictors$water_quality$water_quality_PC1),100))
predicted_water_quality2 <- predict.manyglm(varpart_peixes$models$water_quality, newdata = newdata_water_quality2, type = "response")

line_tp_water_quality2 <- rep(5, ncol(predicted_water_quality2))
line_tp_water_quality2[which(water_quality_2_lower_coefs > 0)] <- 1
line_tp_water_quality2[which(water_quality_2_upper_coefs < 0 )] <- 1

lwd_water_quality2 <- rep(3, ncol(predicted_water_quality2))
lwd_water_quality2[which(water_quality_2_lower_coefs > 0)] <- 4
lwd_water_quality2[which(water_quality_2_upper_coefs < 0 )] <- 4


###################################################

newdata_hydrology1 <- data.frame(hydrology_PC1 = seq(from = min(predictors$hydrology$hydrology_PC1), to = max(predictors$hydrology$hydrology_PC1), length.out = 100),
                           hydrology_PC2 = rep(median(predictors$hydrology$hydrology_PC2),100))
predicted_hydrology1 <- predict.manyglm(varpart_peixes$models$hydrology, newdata = newdata_hydrology1, type = "response")

line_tp_hydrology1 <- rep(5, ncol(predicted_hydrology1))
line_tp_hydrology1[which(hydrology_lower_coefs > 0)] <- 1
line_tp_hydrology1[which(hydrology_upper_coefs < 0)] <- 1

lwd_hydrology1 <- rep(3, ncol(predicted_hydrology1))
lwd_hydrology1[which(hydrology_lower_coefs > 0)] <- 4
lwd_hydrology1[which(hydrology_upper_coefs < 0)] <- 4

###################################################

modelo_hydrology <- manyglm(assembleia_peixes_rm_mv ~ hydrology_PC1 + hydrology_PC2, data = predictors$hydrology, family = "negative.binomial")

newdata_hydrology2 <- data.frame(hydrology_PC2 = seq(from = min(predictors$hydrology$hydrology_PC2), to = max(predictors$hydrology$hydrology_PC2), length.out = 100),
                           hydrology_PC1 = rep(median(predictors$hydrology$hydrology_PC1),100))

predicted_hydrology2 <- predict.manyglm(modelo_hydrology, newdata = newdata_hydrology2, type = "response")

line_tp_hydrology2 <- rep(5, ncol(predicted_hydrology2))
line_tp_hydrology2[which(hydrology_2_lower_coefs > 0)] <- 1
line_tp_hydrology2[which(hydrology_2_upper_coefs < 0 )] <- 1

lwd_hydrology2 <- rep(3, ncol(predicted_hydrology2))
lwd_hydrology2[which(hydrology_2_lower_coefs > 0)] <- 4
lwd_hydrology2[which(hydrology_2_upper_coefs < 0 )] <- 4



poecilidae <- which(colnames(predicted_est1) == "Phalloceros_reisi" | colnames(predicted_est1) == "Phalloceros_harpagos" | colnames(predicted_est1) == "Poecilia_reticulata" | colnames(predicted_est1) == "Poecilia_vivipara")
NOT_poecilidae <- which(colnames(predicted_est1) != "Phalloceros_reisi" & colnames(predicted_est1) != "Phalloceros_harpagos" & colnames(predicted_est1) != "Poecilia_reticulata" & colnames(predicted_est1) != "Poecilia_vivipara")

```



## Plot

```{r,   fig.width = 7, fig.height = 10, dpi = 600, dev.args= list(pointsize=8), eval = TRUE, echo = TRUE}

#svg("plots/predictions.svg", width = 11, height = 10, pointsize = 13)



close.screen(all.screens = TRUE)
split.screen(matrix(c(0  , 0.5, 0.7333334, 1,
                      0.5, 1  , 0.7333334, 1, 
                      0  , 0.5, 0.4666667, 0.7333334,
                      0.5, 1  , 0.4666667, 0.7333334,
                      0,   0.5, 0.2, 0.4666667,
                      0.5,   1  , 0.2, 0.4666667,
                      0, 1, 0, 0.2), ncol = 4, nrow = 7, byrow = TRUE))


###################################################################### FIRST PLOT


###################################################################### SECOND PLOT
screen(1)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,20), xlim = c(min(newdata_est1$est_PC1),max(newdata_est1$est_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_est1[,NOT_poecilidae])){
  lines(x = newdata_est1$est_PC1, y = predicted_est1[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est1$est_PC1, y = predicted_est1[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_est1[NOT_poecilidae][i], lty = line_tp_est1[NOT_poecilidae][i])
}

axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_est1$est_PC1),max(newdata_est1$est_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_est1[,poecilidae])){
  lines(x = newdata_est1$est_PC1, y = predicted_est1[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est1$est_PC1, y = predicted_est1[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_est1[poecilidae][i], lty = line_tp_est1[poecilidae][i])
}

axis(4, labels = FALSE, at = c(0, 150, 300, 450, 600))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, at = c(0, 150, 300, 450, 600), gap.axis = -10)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Rubble and rubbish", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_est1$est_PC1)+0.4)
mtext("Swage pipes",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_est1$est_PC1)+0.4)
#mtext("outside the channel",       side = 1, line = 1.5    , adj = 1, cex = 0.8, at = max(newdata_est$est_PC1)+0.4)

mtext("Arboreal vegetation", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_est1$est_PC1)-0.4)


title(xlab = "Structural", line = 0.5)
title(xlab = "complexity", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "a)", cex = 1.5)


###################################################################### SECOND PLOT
screen(2)



par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,20), xlim = c(min(newdata_est2$est_PC2),max(newdata_est2$est_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_est2[,NOT_poecilidae])){
  lines(x = newdata_est2$est_PC2, y = predicted_est2[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est2$est_PC2, y = predicted_est2[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_est2[NOT_poecilidae][i], lty = line_tp_est2[NOT_poecilidae][i])
}

axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_est2$est_PC2),max(newdata_est2$est_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_est2[,poecilidae])){
  lines(x = newdata_est2$est_PC2, y = predicted_est2[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_est2$est_PC2, y = predicted_est2[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_est2[poecilidae][i], lty = line_tp_est2[poecilidae][i])
}

axis(4, labels = FALSE, at = c(0, 150, 300, 450, 600))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, at = c(0, 150, 300, 450, 600), gap.axis = -10)

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Continuous flow", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_est2$est_PC2)+0.4)
mtext("Grasses at the margins",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_est2$est_PC2)+0.4)
mtext("Muddy substrate",   side = 1, line = 1.5    , adj = 1, cex = 0.8, at = max(newdata_est2$est_PC2)+0.4)

mtext("Rapids and pools", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_est2$est_PC2)-0.4)
mtext("Rocky substrate", side = 1, line = 0.75 , adj = 0, cex = 0.8, at = min(newdata_est2$est_PC2)-0.4)


title(xlab = "Structural", line = 0.5)
title(xlab = "complexity", line = 1.5)
title(xlab = "(PC2)", line = 2.5)

letters(x = 5, y = 95, "b)", cex = 1.5)


###################################################################### THIRD PLOT

screen(3)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,20), xlim = c(min(newdata_water_quality1$water_quality_PC1),max(newdata_water_quality1$water_quality_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_water_quality1[,NOT_poecilidae])){
  lines(x = newdata_water_quality1$water_quality_PC1, y = predicted_water_quality1[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_water_quality1$water_quality_PC1, y = predicted_water_quality1[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_water_quality1[NOT_poecilidae][i], lty = line_tp_water_quality1[NOT_poecilidae][i])
}

axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_water_quality1$water_quality_PC1),max(newdata_water_quality1$water_quality_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_water_quality1[,poecilidae])){
  lines(x = newdata_water_quality1$water_quality_PC1, y = predicted_water_quality1[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_water_quality1$water_quality_PC1, y = predicted_water_quality1[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_water_quality1[poecilidae][i], lty = line_tp_water_quality1[poecilidae][i])
}

axis(4, labels = FALSE, gap.axis= -10, at = c(0, 150, 300, 450, 600))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10, at = c(0, 150, 300, 450, 600))

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Higher conductivity",       side = 1, line = 0    , adj = 1, cex = 0.8, at = max(newdata_water_quality1$water_quality_PC1)+0.4)
mtext("More total dissolved C and N",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_water_quality1$water_quality_PC1)+0.4)
mtext("More chlorophyll-a", side = 1, line = 1.5 , adj = 1, cex = 0.8, at = max(newdata_water_quality1$water_quality_PC1)+0.4)


mtext("Greater dissolved Oxigen", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_water_quality1$water_quality_PC1)-0.4)
mtext("Greater redox potential", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_water_quality1$water_quality_PC1)-0.4)

title(xlab = "Water", line = 0.5)
title(xlab = "quality", line = 1.5)
title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "c)", cex = 1.5)



###################################################################### THIRD PLOT

screen(4)


par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,20), xlim = c(min(newdata_water_quality2$water_quality_PC2),max(newdata_water_quality2$water_quality_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_water_quality2[,NOT_poecilidae])){
  lines(x = newdata_water_quality2$water_quality_PC2, y = predicted_water_quality2[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_water_quality2$water_quality_PC2, y = predicted_water_quality2[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_water_quality2[NOT_poecilidae][i], lty = line_tp_water_quality2[NOT_poecilidae][i])
}

axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_water_quality2$water_quality_PC2),max(newdata_water_quality2$water_quality_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_water_quality2[,poecilidae])){
  lines(x = newdata_water_quality2$water_quality_PC2, y = predicted_water_quality2[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_water_quality2$water_quality_PC2, y = predicted_water_quality2[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_water_quality2[poecilidae][i], lty = line_tp_water_quality2[poecilidae][i])
}

axis(4, labels = FALSE, gap.axis= -10, at = c(0, 150, 300, 450, 600))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10, at = c(0, 150, 300, 450, 600))

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Turbid waters",       side = 1, line = 0    , adj = 1, cex = 0.8, at = max(newdata_water_quality2$water_quality_PC2)+0.4)
mtext("Greater redox potential",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_water_quality2$water_quality_PC2)+0.4)

mtext("Higher temperature", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_water_quality2$water_quality_PC2)-0.4)

title(xlab = "Water", line = 0.5)
title(xlab = "quality", line = 1.5)
title(xlab = "(PC2)", line = 2.5)


letters(x = 5, y = 95, "d)", cex = 1.5)



###################################################################### FOURTH PLOT


screen(5)

par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,20), xlim = c(min(newdata_hydrology1$hydrology_PC1),max(newdata_hydrology1$hydrology_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_hydrology1[,NOT_poecilidae])){
  lines(x = newdata_hydrology1$hydrology_PC1, y = predicted_hydrology1[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_hydrology1$hydrology_PC1, y = predicted_hydrology1[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_hydrology1[NOT_poecilidae][i], lty = line_tp_hydrology1[NOT_poecilidae][i])
}

axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_hydrology1$hydrology_PC1),max(newdata_hydrology1$hydrology_PC1)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_hydrology1[,poecilidae])){
  lines(x = newdata_hydrology1$hydrology_PC1, y = predicted_hydrology1[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_hydrology1$hydrology_PC1, y = predicted_hydrology1[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_hydrology1[poecilidae][i], lty = line_tp_hydrology1[poecilidae][i])
}

axis(4, labels = FALSE, gap.axis= -10, at = c(0, 150, 300, 450, 600))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10, at = c(0, 150, 300, 450, 600))

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Larger catchment area", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_hydrology1$hydrology_PC1)+0.4)
mtext("Greater discharge",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_hydrology1$hydrology_PC1)+0.4)
mtext("Elongated catchments",       side = 1, line = 1.5    , adj = 1, cex = 0.8, at = max(newdata_hydrology1$hydrology_PC1)+0.4)


mtext("Circular catchments", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_hydrology1$hydrology_PC1)-0.4)
mtext("Narrower channels", side = 1, line = 0.75 , adj = 0, cex = 0.8, at = min(newdata_hydrology1$hydrology_PC1)-0.4)

title(xlab = "Hydrology", line = 0.5)
title(xlab = "(PC1)", line = 1.5)
#title(xlab = "(PC1)", line = 2.5)

letters(x = 5, y = 95, "e)", cex = 1.5)




###################################################################### FOURTH PLOT


screen(6)


par(mar = c(4,4,1,4), bty = "u")
plot(NA, ylim = c(0,20), xlim = c(min(newdata_hydrology2$hydrology_PC2),max(newdata_hydrology2$hydrology_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")


for(i in 1:ncol(predicted_hydrology2[,NOT_poecilidae])){
  lines(x = newdata_hydrology2$hydrology_PC2, y = predicted_hydrology2[,NOT_poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_hydrology2$hydrology_PC2, y = predicted_hydrology2[,NOT_poecilidae][,i], col = colors[NOT_poecilidae][i], lwd = lwd_hydrology2[NOT_poecilidae][i], lty = line_tp_hydrology2[NOT_poecilidae][i])
}

axis(2, labels = FALSE, gap.axis= -10)
axis(2, labels = TRUE, tick = FALSE, line = -0.5, gap.axis= -10)

par(new = TRUE)
plot(NA, ylim = c(0,700), xlim = c(min(newdata_hydrology2$hydrology_PC2),max(newdata_hydrology2$hydrology_PC2)), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

for(i in 1:ncol(predicted_hydrology2[,poecilidae])){
  lines(x = newdata_hydrology2$hydrology_PC2, y = predicted_hydrology2[,poecilidae][,i], col = "white", lwd = 5)
  lines(x = newdata_hydrology2$hydrology_PC2, y = predicted_hydrology2[,poecilidae][,i], col = colors[poecilidae][i], lwd = lwd_hydrology2[poecilidae][i], lty = line_tp_hydrology2[poecilidae][i])
}

axis(4, labels = FALSE, at = c(0, 150, 300, 450, 600))
axis(4, labels = TRUE, tick = FALSE, line = -0.5, at = c(0, 150, 300, 450, 600))

mtext("Abundance", side = 2, line = 2)
mtext("Abundance*", side = 4, line = 2)

#axis(1, labels = FALSE)
#axis(1, labels = TRUE, tick = FALSE, line = -0.5)

mtext("Steeper slopes", side = 1, line = 0 , adj = 1, cex = 0.8, at = max(newdata_hydrology2$hydrology_PC2)+0.4)
mtext("Higher altitudes",       side = 1, line = 0.75    , adj = 1, cex = 0.8, at = max(newdata_hydrology2$hydrology_PC2)+0.4)

mtext("Greater water velocity", side = 1, line = 0 , adj = 0, cex = 0.8, at = min(newdata_hydrology2$hydrology_PC2)-0.4)
mtext("Shallower channels", side = 1, line = 0.75 , adj = 0, cex = 0.8,  at = min(newdata_hydrology2$hydrology_PC2)-0.4)

title(xlab = "Hydrology", line = 0.5)
title(xlab = "(PC2)", line = 1.5)

letters(x = 5, y = 95, "f)", cex = 1.5)



###################################################################### FOURTH PLOT

###################################################################### FOURTH PLOT




###################################################################### 
screen(7)
par(mar = c(0,0,0,0))
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", , xaxs = "i", yaxs = "i", bty = "n")

font <- rep(3, length(names))
font[which(names == "Singletons")] <- 1

legend(x = 50, y = 50, col = colors, lty = 1, lwd = 4, legend = names, ncol = 3, xjust = 0.5, yjust = 0.5, box.lty = 0, text.font = font, x.intersp	
= 1)

#dev.off()
  


```



