---
title: "Environmental PCAs - North vs South"
author: "Rodolfo Pelinson"
date: "`r Sys.Date()`"
output: 
  github_document: 
    fig_width: 5
    fig_height: 15
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE}
dir<-("C:/Users/rodol/OneDrive/repos/Urban_fish_assemblages")
```

Loading important functions and packages

```{r, message = FALSE, warning = FALSE}
library(vegan)
library(yarrr)
library(greekLetters)
library(scales)
library(shape)

source(paste(sep = "/",dir,"functions/text_contour.R"))
source(paste(sep = "/",dir,"functions/text_repositioning.R"))

```


```{r}

assembleia_peixes <- read.csv(paste(sep = "/",dir,"data/com_por_bacia.csv"), row.names = 1)

agua <-read.csv(paste(sep = "/",dir,"data/planilha_agua_assembleias.csv"), row.names = 1)
estrutura <-read.csv(paste(sep = "/",dir,"data/planilha_estrutura_assembleias.csv"), row.names = 1)
bacia <- read.csv(paste(sep = "/",dir,"data/planilha_bacia_assembleias.csv"), row.names = 1)
```

Removing urban cover from watershed descriptors, and a few other predictors that are redundant
```{r}
urb <- bacia$urbano_delineamento
bacia <- bacia[colnames(bacia) != "urbano_delineamento" &
                 colnames(bacia) != "URB_2021"]
names(urb) <- rownames(bacia)

estrutura <- estrutura[colnames(estrutura) != "descarga_vel_dim" &
                   colnames(estrutura) != "descarga_.L.s_sal"&
                   colnames(estrutura) != "descarga_.L.s_sal"]

```


```{r}
comp_ecotono_arborea <- estrutura$comp_ecotono_arborea + estrutura$comp_ecotono_arbustiva + estrutura$comp_ecotono_pendurada
comp_ecotono_raizes <- estrutura$comp_ecotono_raizes_finas_em_rede + estrutura$comp_ecotono_raizes_grandes
comp_ecotono_grasses <- estrutura$comp_ecotono_gramineas + estrutura$comp_ecotono_vegetacao_herbacea + estrutura$comp_ecotono_herbacea_ereta
comp_ecotono_aquatic_veg <- estrutura$comp_ecotono_submersa + estrutura$comp_ecotono_flutuante
comp_ecotono_anthropic_complex_est <- estrutura$comp_ecotono_entulho + estrutura$comp_ecotono_arame


estrutura <- estrutura[,-which(colnames(estrutura) %in% c("comp_ecotono_arbustiva",
                                "comp_ecotono_arborea",
                                "comp_ecotono_gramineas",
                                "comp_ecotono_vegetacao_herbacea",
                                "comp_ecotono_herbacea_ereta",
                                "comp_ecotono_pendurada",
                                "comp_ecotono_submersa",
                                "comp_ecotono_flutuante",
                                "comp_ecotono_entulho",
                                "comp_ecotono_arame",
                                "comp_ecotono_raizes_finas_em_rede",
                                "comp_ecotono_raizes_grandes"))]

estrutura <- cbind(estrutura, comp_ecotono_arborea, comp_ecotono_raizes, comp_ecotono_grasses, comp_ecotono_aquatic_veg, comp_ecotono_anthropic_complex_est)

colnames(estrutura)

```


```{r}
substrato_areia <- estrutura$substrato_silte + estrutura$substrato_areia

substrato_cascalho <- estrutura$substrato_cascalho + estrutura$substrato_seixo

substrato_litter <- estrutura$substrato_litter + estrutura$substrato_litter_grosseiro

substrato_galhos_troncos <-  estrutura$substrato_galhos_grandes_troncos + estrutura$substrato_galhos_pequenos

substrato_entulho <-  estrutura$substrato_entulho + estrutura$substrato_arame


estrutura <- estrutura[,-which(colnames(estrutura) %in% c("substrato_silte",
                                                         "substrato_areia",
                                "substrato_cascalho",
                                "substrato_seixo",
                                "substrato_litter",
                                "substrato_litter_grosseiro",
                                "substrato_galhos_grandes_troncos",
                                "substrato_galhos_pequenos",
                                "substrato_entulho",
                                "substrato_arame"))]
                                

estrutura <- cbind(estrutura, substrato_areia, substrato_cascalho, substrato_litter, substrato_galhos_troncos, substrato_entulho)

```

```{r}

comp_zona_riparia_veg_arborea <- estrutura$comp_zona_riparia_veg_arborea + estrutura$comp_zona_riparia_veg_arbustiva

comp_zona_riparia_grasses <- estrutura$comp_zona_riparia_veg_herbacea + estrutura$comp_zona_riparia_veg_herb_ereta + estrutura$comp_zona_riparia_graminea

comp_zona_riparia_const_anthr <- estrutura$comp_zona_riparia_calcada + estrutura$comp_zona_riparia_asfalto + estrutura$comp_zona_riparia_constucao + estrutura$comp_zona_riparia_canal_vert + estrutura$comp_zona_riparia_grade_arame

comp_zona_riparia_agriculture <- estrutura$comp_zona_riparia_plantacao + estrutura$comp_zona_riparia_pastagem

estrutura <- estrutura[,-which(colnames(estrutura) %in% c("comp_zona_riparia_veg_arborea",                      
                                "comp_zona_riparia_veg_arbustiva",
                                "comp_zona_riparia_veg_herbacea",                     
                                "comp_zona_riparia_veg_herb_ereta",            
                                "comp_zona_riparia_graminea",
                                "comp_zona_riparia_calcada",                          
                                "comp_zona_riparia_asfalto",
                                "comp_zona_riparia_constucao",                        
                                "comp_zona_riparia_canal_vert",                       
                                "comp_zona_riparia_grade_arame",
                                "comp_zona_riparia_plantacao",                        
                                "comp_zona_riparia_pastagem"))]

estrutura <- cbind(estrutura, comp_zona_riparia_veg_arborea, comp_zona_riparia_grasses, comp_zona_riparia_const_anthr, comp_zona_riparia_agriculture)

```



```{r}
pert_zona_riparia_entulho_e_lixo <- estrutura$pert_zona_riparia_entulho + estrutura$pert_zona_riparia_lixo_inorganico

pert_zona_riparia_construções <- estrutura$pert_zona_riparia_construcoes + estrutura$pert_zona_riparia_bomba

estrutura <- estrutura[,-which(colnames(estrutura) %in% c("pert_zona_riparia_entulho",
                                "pert_zona_riparia_lixo_inorganico",
                                "pert_zona_riparia_construcoes",
                                "pert_zona_riparia_bomba"))]


estrutura <- cbind(estrutura, pert_zona_riparia_entulho_e_lixo, pert_zona_riparia_construções)

```



```{r}
estrutura_dentro_do_canal_pedaco_de_madeira <- estrutura$estrutura_dentro_do_canal_pedaco_de_madeira_grande + estrutura$estrutura_dentro_do_canal_pedaco_de_madeira_pequeno

estrutura_dentro_do_canal_macrofitas_e_raizes <- estrutura$estrutura_dentro_do_canal_raizes_vivas + estrutura$estrutura_dentro_do_canal_vegetacao_pendurada + estrutura$estrutura_dentro_do_canal_macrofita

estrutura_dentro_do_canal_grasses <- estrutura$estrutura_dentro_do_canal_herb_ereta + estrutura$estrutura_dentro_do_canal_graminea

estrutura_dentro_do_canal_entulho_e_lixo <- estrutura$estrutura_dentro_do_canal_entulho + estrutura$estrutura_dentro_do_canal_lixo_inorganico

estrutura <- estrutura[,-which(colnames(estrutura) %in% c("estrutura_dentro_do_canal_pedaco_de_madeira_grande", 
                                "estrutura_dentro_do_canal_pedaco_de_madeira_pequeno",
                                "estrutura_dentro_do_canal_raizes_vivas",
                                "estrutura_dentro_do_canal_vegetacao_pendurada", 
                                "estrutura_dentro_do_canal_macrofita", 
                                "estrutura_dentro_do_canal_herb_ereta",               
                                "estrutura_dentro_do_canal_graminea",   
                                "estrutura_dentro_do_canal_entulho",                  
                                "estrutura_dentro_do_canal_lixo_inorganico"))]

estrutura <- cbind(estrutura, estrutura_dentro_do_canal_pedaco_de_madeira, estrutura_dentro_do_canal_macrofitas_e_raizes, estrutura_dentro_do_canal_grasses, estrutura_dentro_do_canal_entulho_e_lixo)

         
              

```



```{r}
vars <- colnames(estrutura)
estrutura <- estrutura[,order(vars)]
```


# Sctructural complexity
```{r}
colnames(estrutura)
colnames(bacia)
colnames(agua)

structural_complexity_vars <- c("dossel",
                                "comp_ecotono_anthropic_complex_est",          
                                "comp_ecotono_aquatic_veg",                     
                                "comp_ecotono_arborea",                         
                                "comp_ecotono_concreto",                        
                                "comp_ecotono_grasses",                         
                                "comp_ecotono_raizes",                          
                                "comp_ecotono_rocha",                           
                                "comp_ecotono_solo_exposto",
                                
                                "substrato_areia",                              
                                "substrato_argila",                             
                                "substrato_cascalho",                           
                                "substrato_concreto" ,                          
                                "substrato_entulho"  ,                          
                                "substrato_galhos_troncos" ,                    
                                "substrato_litter"    ,                         
                                "substrato_lodo" ,                              
                                "substrato_matacao" ,                           
                                "substrato_rocha",
                                
                                "tipo_de_canal_corredeira",
                                "tipo_de_canal_poco",
                                "tipo_de_canal_cascata",
                                "tipo_de_canal_fluxo_continuo",
                                
                                "pert_zona_riparia_animais_criacao",            
                                "pert_zona_riparia_cano_esgoto",                
                                "pert_zona_riparia_construções",                
                                "pert_zona_riparia_entulho_e_lixo"  ,           
                                "pert_zona_riparia_lixo_organico" ,
                                
                                "comp_zona_riparia_agriculture",                
                                "comp_zona_riparia_area_alagada",               
                                "comp_zona_riparia_const_anthr",                
                                "comp_zona_riparia_grasses",                    
                                "comp_zona_riparia_solo_exposto",               
                                "comp_zona_riparia_veg_arborea",
                                
                                "estrutura_dentro_do_canal_banco_de_folhas",    
                                "estrutura_dentro_do_canal_banco_de_terra",     
                                "estrutura_dentro_do_canal_cianobacterias",     
                                "estrutura_dentro_do_canal_entulho_e_lixo",     
                                "estrutura_dentro_do_canal_grasses",            
                                "estrutura_dentro_do_canal_macrofitas_e_raizes",
                                "estrutura_dentro_do_canal_matacao",            
                                "estrutura_dentro_do_canal_pedaco_de_madeira"#,
                                
                               #"encaixe_rocha",                                      
                               #"encaixe_vale",                                       
                               #"encaixe_terraco",                                    
                               #"encaixe_alt_antropica",                              
                               #"encaixe_sem_feicoes",                                
                                #"tipo_de_encaixe_vale_em_U",                          
                                #"tipo_de_encaixe_concavo",                            
                                #"tipo_de_encaixe_vale_assimetrico"
                               )


hydrology_vars <- c("nova_descarga_sal",
                    "sinuosidade",
                    "prof_media",
                    "larg_media",
                    "velocidade_media",
                    "Area_ha",
                    "Ic",
                    "Kc",
                    "Declividade_av",
                    "tipo_de_encaixe_encaixado_canalizado"#,               
                    #"Altitude_av",
                    )

water_quality_vars <- c("chlorophyll_a",
                    "phycocyanin",
                    "Temperature_.oC.",
                    "DO_.mg.L.",
                    "pH",
                    "turbidity_.NTU.",
                    "redox_potential_.mV.",
                    "TC",
                    "TN",
                    "SPC_.uS.cm.")
```


```{r}
#Join all variables
env_pred <- cbind(estrutura, bacia, agua)

structural_complexity <- env_pred[,which(colnames(env_pred) %in% structural_complexity_vars)]
hydrology <- env_pred[,which(colnames(env_pred) %in% hydrology_vars)]
water_quality <- env_pred[,which(colnames(env_pred) %in% water_quality_vars)]


```


Standardizing predictors
```{r}
structural_complexity_st <- decostand(structural_complexity, method = "stand")
hydrology_st <- decostand(hydrology, method = "stand")
water_quality_st <- decostand(water_quality, method = "stand")


#numero de colunas de cada uma
ncol(water_quality_st)
ncol(structural_complexity_st)
ncol(hydrology_st)

```


### PCA structural complexity

```{r}
pca_structural_complexity <- rda(structural_complexity_st)

importance_structural_complexity <- round(pca_structural_complexity$CA$eig/sum(pca_structural_complexity$CA$eig),2)
Eigenvalues_structural_complexity <- data.frame(autovalores = pca_structural_complexity$CA$eig,
                                    importance = importance_structural_complexity)

Eigenvalues_structural_complexity
sum(importance_structural_complexity[1:2])

structural_complexity_PCs <- pca_structural_complexity$CA$u
#structural_complexity_PCs[,1] <- structural_complexity_PCs[,1]*-1
structural_complexity_loadings <- pca_structural_complexity$CA$v
#structural_complexity_loadings[,1] <- structural_complexity_loadings[,1]*-1
  
structural_complexity_loadings_filtrados <- structural_complexity_loadings[which((structural_complexity_loadings[,1] > 0.2 | structural_complexity_loadings[,1] < -0.2) |
                                                         (structural_complexity_loadings[,2] > 0.2 | structural_complexity_loadings[,2] < -0.2)),1:2]
structural_complexity_loadings_filtrados

urb_cors_structural_complexity <- rep(NA, ncol(structural_complexity_PCs))
for(i in 1:ncol(structural_complexity_PCs)){
  urb_cors_structural_complexity[i] <- cor(structural_complexity_PCs[,i], urb)
}

#write.csv(Eigenvalues_structural_complexity, "data/pcas_amb/structural_complexity_autovalores.csv")
#write.csv(structural_complexity_PCs, "data/pcas_amb/structural_complexity_PCs.csv")
#write.csv(structural_complexity_loadings, "data/pcas_amb/structural_complexity_loadings.csv")

```


Preparing variables for plotting the PCA

```{r}
#Plot parameters
scaler <- min(max(abs(structural_complexity_PCs[, 1]))/max(abs(structural_complexity_loadings_filtrados[,1])),
              max(abs(structural_complexity_PCs[, 2]))/max(abs(structural_complexity_loadings_filtrados[,2])))

structural_complexity_loadings_filtrados_new <- structural_complexity_loadings_filtrados * scaler * 0.8

#structural_complexity_PCs <- jitter(structural_complexity_PCs, amount = 0.1)

pc1_label_structural_complexity <- paste("PC1 (",round(importance_structural_complexity[1]*100,2),"%)", " (", greeks("rho"), " = ", round(urb_cors_structural_complexity[1], 3), ")", sep = "")

pc2_label_structural_complexity <- paste("PC2 (",round(importance_structural_complexity[2]*100,2),"%)", " (", greeks("rho"), " = ", round(urb_cors_structural_complexity[2], 3), ")", sep = "")

#xmin <- min(c(structural_complexity_PCs[,1], structural_complexity_loadings_filtrados_new[,1]))*1.1
#xmax <- max(c(structural_complexity_PCs[,1], structural_complexity_loadings_filtrados_new[,1]))*1.1
#ymin <- min(c(structural_complexity_PCs[,2], structural_complexity_loadings_filtrados_new[,2]))*1.1
#ymax <- max(c(structural_complexity_PCs[,2], structural_complexity_loadings_filtrados_new[,2]))*1.1



#Plot########################################################################################
names_structural_complexity <- rownames(structural_complexity_loadings_filtrados_new)

names_structural_complexity[names_structural_complexity == "comp_ecotono_grasses"] <- "Marginal grasses"
names_structural_complexity[names_structural_complexity == "comp_ecotono_arborea"] <- "Marginal arboreal veg."
names_structural_complexity[names_structural_complexity == "comp_ecotono_aquatic_veg"] <- "Marginal aquatic veg."
names_structural_complexity[names_structural_complexity == "comp_ecotono_raizes"] <- "Marginal roots"

names_structural_complexity[names_structural_complexity == "substrato_rocha"] <- "Rocky substrate"
names_structural_complexity[names_structural_complexity == "substrato_argila"] <- "Muddy substrate"

names_structural_complexity[names_structural_complexity == "tipo_de_canal_corredeira"] <- "Rapids"
names_structural_complexity[names_structural_complexity == "tipo_de_canal_poco"] <- "Pools"
names_structural_complexity[names_structural_complexity == "tipo_de_canal_fluxo_continuo"] <- "Continuous flow"

names_structural_complexity[names_structural_complexity == "pert_zona_riparia_cano_esgoto"] <- "Swage pipes on RZ"
#names_structural_complexity[names_structural_complexity == "pert_zona_riparia_lixo_inorganico"] <- "Inorganic waste on RZ"
names_structural_complexity[names_structural_complexity == "pert_zona_riparia_entulho_e_lixo"] <- "Rubble and rubbish IC"
names_structural_complexity[names_structural_complexity == "comp_zona_riparia_veg_arborea"] <- "Arboreal vegetation RZ"
names_structural_complexity[names_structural_complexity == "comp_zona_riparia_const_anthr"] <- "Rubble and rubbish RZ"
names_structural_complexity[names_structural_complexity == "comp_zona_riparia_grasses"] <- "Grasses RZ"

#names_structural_complexity[names_structural_complexity == "estrutura_dentro_do_canal_entulho"] <- "Construction waste inside"
#names_structural_complexity[names_structural_complexity == "estrutura_dentro_do_canal_lixo_inorganico"] <- "Inorganic waste inside"

names_structural_complexity[names_structural_complexity == "encaixe_vale"] <- "Valley channel confinement"
names_structural_complexity[names_structural_complexity == "encaixe_alt_antropica"] <- "Anthr. channel confinement"
names_structural_complexity[names_structural_complexity == "tipo_de_encaixe_vale_em_U"] <- "U shaped channel confinement"

names_structural_complexity[names_structural_complexity == "estrutura_dentro_do_canal_entulho_e_lixo"] <- "Rubble and rubbish IC"
names_structural_complexity[names_structural_complexity == "estrutura_dentro_do_canal_macrofitas_e_raizes"] <- "Macrophytes and roots IC"
names_structural_complexity[names_structural_complexity == "estrutura_dentro_do_canal_pedaco_de_madeira"] <- "Wood pieces IC"


```



### PCA Hydrology

```{r}
pca_hydrology <- rda(hydrology_st)

importance_hydrology <- round(pca_hydrology$CA$eig/sum(pca_hydrology$CA$eig),2)

cumulative_importance_hydrology <- rep(NA, length(importance_hydrology))
exp_importance_hydrology <- rep(NA, length(importance_hydrology))

cumulative_importance_hydrology[1] <- importance_hydrology[1]
#exp_importance_hydrology[1] <- importance_hydrology[1]
for(i in 2:length(importance_hydrology)){
  cumulative_importance_hydrology[i] <- cumulative_importance_hydrology[i-1] + importance_hydrology[i]
#  exp_importance_hydrology[i] <- importance_hydrology[i-1]/2
}


Eigenvalues_hydrology <- data.frame(autovalores = pca_hydrology$CA$eig,
                                    importance = importance_hydrology,
                                cumulative_importance_hydrology)

Eigenvalues_hydrology


Eigenvalues_hydrology
sum(importance_hydrology[1:3])
hydrology_PCs <- pca_hydrology$CA$u
hydrology_PCs[,1] <- hydrology_PCs[,1]*-1
hydrology_loadings <- pca_hydrology$CA$v
hydrology_loadings[,1] <- hydrology_loadings[,1]*-1


hydrology_loadings_filtrados <- hydrology_loadings[which((hydrology_loadings[,1] > 0.2 | hydrology_loadings[,1] < -0.2) |
                                                         (hydrology_loadings[,2] > 0.2 | hydrology_loadings[,2] < -0.2)),1:2]
hydrology_loadings_filtrados

urb_cors_hydrology <- rep(NA, ncol(hydrology_PCs))
for(i in 1:ncol(hydrology_PCs)){
  urb_cors_hydrology[i] <- cor(hydrology_PCs[,i], urb)
}

#write.csv(Eigenvalues_hydrology, "data/pcas_amb/hydrology_autovalores.csv")
#write.csv(hydrology_PCs, "data/pcas_amb/hydrology_PCs.csv")
#write.csv(hydrology_loadings, "data/pcas_amb/hydrology_loadings.csv")
```


Preparing variables for plotting the PCA

```{r}
#Plot parameters
scaler <- min(max(abs(hydrology_PCs[, 1]))/max(abs(hydrology_loadings_filtrados[,1])),
              max(abs(hydrology_PCs[, 2]))/max(abs(hydrology_loadings_filtrados[,2])))

hydrology_loadings_filtrados_new <- hydrology_loadings_filtrados * scaler * 0.8

#hydrology_PCs <- jitter(hydrology_PCs, amount = 0.1)

pc1_label_hydrology <- paste("PC1 (",round(importance_hydrology[1]*100,2),"%)", " (", greeks("rho"), " = ", round(urb_cors_hydrology[1], 3), ")", sep = "")

pc2_label_hydrology <- paste("PC2 (",round(importance_hydrology[2]*100,2),"%)", " (", greeks("rho"), " = ", round(urb_cors_hydrology[2], 3), ")", sep = "")

#xmin <- min(c(hydrology_PCs[,1], hydrology_loadings_filtrados_new[,1]))*1.1
#xmax <- max(c(hydrology_PCs[,1], hydrology_loadings_filtrados_new[,1]))*1.1
#ymin <- min(c(hydrology_PCs[,2], hydrology_loadings_filtrados_new[,2]))*1.1
#ymax <- max(c(hydrology_PCs[,2], hydrology_loadings_filtrados_new[,2]))*1.1



#Plot########################################################################################
names_hydrology <- rownames(hydrology_loadings_filtrados_new)

names_hydrology[names_hydrology == "larg_media"] <- "Width" 
names_hydrology[names_hydrology == "nova_descarga_sal"] <- "Discharge"
names_hydrology[names_hydrology == "prof_media"] <- "Depth"
names_hydrology[names_hydrology == "sinuosidade"] <- "Sinuosity"
names_hydrology[names_hydrology == "velocidade_media"] <- "Water velocity"
names_hydrology[names_hydrology == "Area_ha"] <- "Area"
names_hydrology[names_hydrology == "Ic"] <- "IC"
names_hydrology[names_hydrology == "Kc"] <- "KC"
names_hydrology[names_hydrology == "Declividade_av"] <- "Slope"
names_hydrology[names_hydrology == "tipo_de_encaixe_encaixado_canalizado"] <- "Channelized channel"


```


### PCA water quality

```{r}
pca_water_quality <- rda(water_quality_st)

importance_water_quality <- round(pca_water_quality$CA$eig/sum(pca_water_quality$CA$eig),2)
Eigenvalues_water_quality <- data.frame(autovalores = pca_water_quality$CA$eig,
                                importance = importance_water_quality)
Eigenvalues_water_quality

sum(importance_water_quality[1:2])
water_quality_PCs <- pca_water_quality$CA$u
water_quality_loadings <- pca_water_quality$CA$v

water_quality_loadings_filtrados <- water_quality_loadings[which((water_quality_loadings[,1] > 0.2 | water_quality_loadings[,1] < -0.2) |
                                                         (water_quality_loadings[,2] > 0.2 | water_quality_loadings[,2] < -0.2)),1:2]

water_quality_loadings_filtrados


urb_cors_water_quality <- rep(NA, ncol(water_quality_PCs))
for(i in 1:ncol(water_quality_PCs)){
  urb_cors_water_quality[i] <- cor(water_quality_PCs[,i], urb)
}
#write.csv(Eigenvalues_water_quality, "data/pcas_amb/water_quality_autovalores.csv")
#write.csv(water_quality_PCs, "data/pcas_amb/water_quality_PCs.csv")
#write.csv(water_quality_loadings, "data/pcas_amb/water_quality_loadings.csv")
```


Preparing variables for plotting the PCA

```{r}
#Plot parameters
scaler <- min(max(abs(water_quality_PCs[, 1]))/max(abs(water_quality_loadings_filtrados[,1])),
              max(abs(water_quality_PCs[, 2]))/max(abs(water_quality_loadings_filtrados[,2])))

water_quality_loadings_filtrados_new <- water_quality_loadings_filtrados * scaler * 0.8

#water_quality_PCs <- jitter(water_quality_PCs, amount = 0.1)





pc1_label_water_quality <- paste("PC1 (",round(importance_water_quality[1]*100,2),"%)", " (", greeks("rho"), " = ", round(urb_cors_water_quality[1], 3), ")", sep = "")

pc2_label_water_quality <- paste("PC2 (",round(importance_water_quality[2]*100,2),"%)", " (", greeks("rho"), " = ", round(urb_cors_water_quality[2], 3), ")", sep = "")

#xmin <- min(c(water_quality_PCs[,1], water_quality_loadings_filtrados_new[,1]))*1.1
#xmax <- max(c(water_quality_PCs[,1], water_quality_loadings_filtrados_new[,1]))*1.1
#ymin <- min(c(water_quality_PCs[,2], water_quality_loadings_filtrados_new[,2]))*1.1
#ymax <- max(c(water_quality_PCs[,2], water_quality_loadings_filtrados_new[,2]))*1.1



#Plot########################################################################################
names_water_quality <- rownames(water_quality_loadings_filtrados_new)

names_water_quality[names_water_quality == "chlorophyll_a"] <- "Chlorophyll-a" 
names_water_quality[names_water_quality == "phycocyanin"] <- "Phycocyanin"
names_water_quality[names_water_quality == "Temperature_.oC."] <- "Temperature"
names_water_quality[names_water_quality == "pH"] <- "pH"
names_water_quality[names_water_quality == "turbidity_.NTU."] <- "Turbidity"
names_water_quality[names_water_quality == "redox_potential_.mV."] <- "Redox potential"
names_water_quality[names_water_quality == "TC"] <- "TC"
names_water_quality[names_water_quality == "TN"] <- "TN"
names_water_quality[names_water_quality == "SPC_.uS.cm."] <- "Specific conductivity"
names_water_quality[names_water_quality == "DO_.mg.L."] <- "DO"
```



## PCA plots

```{r,   fig.width = 3.5, fig.height = 10.5, dpi = 600, dev.args= list(pointsize=6), eval = TRUE, echo = TRUE}

#svg("plots/pcas_N_S.svg", height = 10.5, width = 3.5, pointsize = 6)

par(mfrow =c(3,1))

par(mar = c(4,4,3,0.1), bty = "o", cex = 1.25)
xmin <- min(c(structural_complexity_PCs[,1], structural_complexity_loadings_filtrados_new[,1]))-0.4
xmax <- max(c(structural_complexity_PCs[,1], structural_complexity_loadings_filtrados_new[,1]))+0.3
ymin <- min(c(structural_complexity_PCs[,2], structural_complexity_loadings_filtrados_new[,2]))-0.1
ymax <- max(c(structural_complexity_PCs[,2], structural_complexity_loadings_filtrados_new[,2]))+0.1

plot(structural_complexity_PCs[,1], structural_complexity_PCs[,2], xlim = c(xmin,xmax), ylim = c(ymin, ymax),
     type = "n", xaxt = "n", yaxt = "n", ylab = "", xlab = "")

abline(h = 0, v = 0, lty = 2)


pal <- col_numeric(palette = c("white", "black"), domain = urb, na.color = "grey50", alpha = FALSE, reverse = FALSE)
col <-pal(urb)

Arrows(x0 <- rep(0, nrow(structural_complexity_loadings_filtrados_new)),
       y0 <- rep(0, nrow(structural_complexity_loadings_filtrados_new)),
       x1 <- structural_complexity_loadings_filtrados_new[,1],
       y1 <- structural_complexity_loadings_filtrados_new[,2], arr.type = "triangle", arr.length = 0.4, col = "#98DF8A", lwd = 1.5)



structural_complexity_loadings_filtrados_new_rp <- text_repositioning(structural_complexity_loadings_filtrados_new, amount = 0.1)
for(i in 1:nrow(structural_complexity_loadings_filtrados_new_rp)){
  text_contour(x = structural_complexity_loadings_filtrados_new_rp[i,1], y = structural_complexity_loadings_filtrados_new_rp[i,2], labels = names_structural_complexity[i], cex = 1, col = "white", font = 2, thick = 0.004)
  
text(x = structural_complexity_loadings_filtrados_new_rp[i,1], y = structural_complexity_loadings_filtrados_new_rp[i,2], labels = names_structural_complexity[i], cex = 1, col = "black", font = 2)
}

points(structural_complexity_PCs[,1],structural_complexity_PCs[,2], col = "black", bg = col, pch = 21, cex = 1.5)
#text(structural_complexity_PCs[,1],structural_complexity_PCs[,2], labels = rownames(structural_complexity_PCs))


#text(x = structural_complexity_loadings_filtrados_new[,1], y = structural_complexity_loadings_filtrados_new[,2], labels = names_structural_complexity, cex = 1, font = 2, xpd = NA)

axis(1, cex.axis = 1.25)
axis(2, cex.axis = 1.25, las = 2)
title(xlab = pc1_label_structural_complexity, cex.lab = 1.4, line = 2.75)
title(ylab = pc2_label_structural_complexity, cex.lab = 1.4, line = 2.75)
title(main = "a) Structural complexity", line = 0.5, adj = 0, cex.main = 1.5)





par(mar = c(4,4,3,0.1), bty = "o", cex = 1.25)
xmin <- min(c(water_quality_PCs[,1], water_quality_loadings_filtrados_new[,1]))-0.1
xmax <- max(c(water_quality_PCs[,1], water_quality_loadings_filtrados_new[,1]))+0.2
ymin <- min(c(water_quality_PCs[,2], water_quality_loadings_filtrados_new[,2]))-0.1
ymax <- max(c(water_quality_PCs[,2], water_quality_loadings_filtrados_new[,2]))+0.05

plot(water_quality_PCs[,1], water_quality_PCs[,2], xlim = c(xmin,xmax), ylim = c(ymin, ymax),
     type = "n", xaxt = "n", yaxt = "n", ylab = "", xlab = "")

abline(h = 0, v = 0, lty = 2)

library(scales)
library(shape)


pal <- col_numeric(palette = c("white", "black"), domain = urb, na.color = "grey50", alpha = FALSE, reverse = FALSE)
col <-pal(urb)

Arrows(x0 <- rep(0, nrow(water_quality_loadings_filtrados_new)),
       y0 <- rep(0, nrow(water_quality_loadings_filtrados_new)),
       x1 <- water_quality_loadings_filtrados_new[,1],
       y1 <- water_quality_loadings_filtrados_new[,2], arr.type = "triangle", arr.length = 0.4, col = "#9EDAE5", lwd = 1.5)


water_quality_loadings_filtrados_new_rp <- text_repositioning(water_quality_loadings_filtrados_new, amount = 0.1)
for(i in 1:nrow(water_quality_loadings_filtrados_new_rp)){
  text_contour(x = water_quality_loadings_filtrados_new_rp[i,1], y = water_quality_loadings_filtrados_new_rp[i,2], labels = names_water_quality[i], cex = 1, col = "white", font = 2, thick = 0.004)
text(x = water_quality_loadings_filtrados_new_rp[i,1], y = water_quality_loadings_filtrados_new_rp[i,2], labels = names_water_quality[i], cex = 1, col = "black", font = 2)
}

points(water_quality_PCs[,1],water_quality_PCs[,2], col = "black", bg = col, pch = 21, cex = 1.5)
#text(water_quality_PCs[,1],water_quality_PCs[,2], labels = rownames(water_quality_PCs))

axis(1, cex.axis = 1.25)
axis(2, cex.axis = 1.25, las = 2)
title(xlab = pc1_label_water_quality, cex.lab = 1.4, line = 2.75)
title(ylab = pc2_label_water_quality, cex.lab = 1.4, line = 2.75)
title(main = "b) Water quality", line = 0.5, adj = 0, cex.main = 1.5)





par(mar = c(4,4,3,0.1), bty = "o", cex = 1.25)
xmin <- min(c(hydrology_PCs[,1], hydrology_loadings_filtrados_new[,1]))-0.1
xmax <- max(c(hydrology_PCs[,1], hydrology_loadings_filtrados_new[,1]))+0.1
ymin <- min(c(hydrology_PCs[,2], hydrology_loadings_filtrados_new[,2]))-0.1
ymax <- max(c(hydrology_PCs[,2], hydrology_loadings_filtrados_new[,2]))+0.02

plot(hydrology_PCs[,1], hydrology_PCs[,2], xlim = c(xmin,xmax), ylim = c(ymin, ymax),
     type = "n", xaxt = "n", yaxt = "n", ylab = "", xlab = "")

abline(h = 0, v = 0, lty = 2)

library(scales)
library(shape)


pal <- col_numeric(palette = c("white", "black"), domain = urb, na.color = "grey50", alpha = FALSE, reverse = FALSE)
col <-pal(urb)

Arrows(x0 <- rep(0, nrow(hydrology_loadings_filtrados_new)),
       y0 <- rep(0, nrow(hydrology_loadings_filtrados_new)),
       x1 <- hydrology_loadings_filtrados_new[,1],
       y1 <- hydrology_loadings_filtrados_new[,2], arr.type = "triangle", arr.length = 0.4, col = "#FFBB78", lwd = 1.5)



hydrology_loadings_filtrados_new_rp <- text_repositioning(hydrology_loadings_filtrados_new, amount = 0.1)
for(i in 1:nrow(hydrology_loadings_filtrados_new_rp)){
  text_contour(x = hydrology_loadings_filtrados_new_rp[i,1], y = hydrology_loadings_filtrados_new_rp[i,2], labels = names_hydrology[i], cex = 1, col = "white", font = 2, thick = 0.004)
text(x = hydrology_loadings_filtrados_new_rp[i,1], y = hydrology_loadings_filtrados_new_rp[i,2], labels = names_hydrology[i], cex = 1, col = "black", font = 2)
}

points(hydrology_PCs[,1],hydrology_PCs[,2], col = "black", bg = col, pch = 21, cex = 1.5)
#text(hydrology_PCs[,1],hydrology_PCs[,2], labels = rownames(hydrology_PCs))


axis(1, cex.axis = 1.25)
axis(2, cex.axis = 1.25, las = 2)
title(xlab = pc1_label_hydrology, cex.lab = 1.4, line = 2.75)
title(ylab = pc2_label_hydrology, cex.lab = 1.4, line = 2.75)
title(main = "c) Hydrology", line = 0.5, adj = 0, cex.main = 1.5)
# dev.off()

```

